---
title: "datapreprocessing clean"
author: "Lucie Kern and Noémie Simon"
format: html
---
---
title: "Data preprocessing and accessibility analysis"
format: html
---

## Load libraries and settings

```{r setup, message=FALSE, warning=FALSE}
library(jsonlite)
library(tidyverse)
library(lubridate)
library(sf)
library(tmap)
library(mapview)
library(nnet)
library(ggplot2)
library(scales)
library(dplyr)
library(tidyr)



knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)

tmap_mode("view")
```

## Create a bibliography for the packages
```{r}
packages_used <- c(
  "jsonlite",
  "tidyverse",
  "dplyr",
  "tidyr",
  "purrr",
  "tibble",
  "lubridate",
  "sf",
  "osmdata",
  "dodgr",
  "ggplot2",
  "tmap",
  "mapview"
)

knitr::write_bib(
  packages_used,
  file = "packages.bib",
  prefix = "R-"
)
```

## Define helper functions and constants

```{r helper-functions}
activity_levels <- c(
  "shopping",
  "nature",
  "healthcare",
  "leisure",
  "sport",
  "education",
  "work",
  "social",
  "home",
  "movement",
  "transport",
  "unknown"
)

analysis_activity_levels <- c(
  "shopping",
  "nature",
  "healthcare",
  "leisure",
  "sport",
  "education",
  "work"
)

home_sf <- st_sf(
  geometry = st_sfc(st_point(c(8.546069, 47.409620))),
  crs = 4326
)

create_output_folders <- function() {
  dir.create("outputs/isochrones_all", recursive = TRUE, showWarnings = FALSE)
  dir.create("outputs/isochrones_sansebike", recursive = TRUE, showWarnings = FALSE)
  dir.create("outputs/pois_all", recursive = TRUE, showWarnings = FALSE)
  dir.create("outputs/pois_sansebike", recursive = TRUE, showWarnings = FALSE)
}

deduplicate_pois <- function(x) {
  dedup_cols <- intersect(
    c("osm_id", "name", "poi_category", "poi_subcategory"),
    names(x)
  )
  
  if (length(dedup_cols) == 0) {
    return(x)
  }
  
  x |>
    distinct(across(all_of(dedup_cols)), .keep_all = TRUE)
}

recode_poi_categories <- function(x) {
  if (!"poi_category_original" %in% names(x)) {
    x <- x |>
      mutate(poi_category_original = poi_category)
  }
  
  x |>
    mutate(
      poi_activity_category = case_when(
        poi_category %in% c("Groceries") ~ "shopping",
        poi_category %in% c("Park / forest") ~ "nature",
        poi_category %in% c("Pharmacy / doctor", "Pharmacy / doctor / doctors") ~ "healthcare",
        poi_category %in% c("Restaurants") ~ "leisure",
        poi_category %in% c("Sport") ~ "sport",
        poi_category %in% c("University") ~ "education",
        poi_category %in% c("Work") ~ "work",
        TRUE ~ "unknown"
      ),
      poi_activity_category = factor(
        poi_activity_category,
        levels = c(analysis_activity_levels, "unknown")
      )
    )
}

is_within_mode <- function(points, polygons, mode_name) {
  polygons_mode <- polygons |>
    filter(mode == mode_name)
  
  lengths(st_within(points, polygons_mode)) > 0
}
```

## Load Google Timeline data

```{r load-google-timeline}
timeline_raw <- fromJSON("timeline.json", flatten = TRUE)

names(timeline_raw)
glimpse(timeline_raw)
```

## Clean Timeline data

```{r clean-timeline-data}
timeline <- timeline_raw |>
  mutate(
    start_time = ymd_hms(startTime),
    end_time = ymd_hms(endTime),
    duration_min = as.numeric(difftime(end_time, start_time, units = "mins")),
    date = as_date(start_time),
    weekday = wday(start_time, label = TRUE, week_start = 1),
    hour = hour(start_time),
    record_type = case_when(
      !is.na(activity.distanceMeters) ~ "movement",
      !is.na(visit.probability) ~ "visit",
      TRUE ~ "unknown"
    ),
    location = case_when(
      record_type == "movement" ~ activity.start,
      record_type == "visit" ~ visit.topCandidate.placeLocation,
      TRUE ~ NA_character_
    ),
    lat = as.numeric(str_extract(location, "(?<=geo:)[0-9.-]+")),
    lon = as.numeric(str_extract(location, "(?<=,)[0-9.-]+")),
    transport_mode = activity.topCandidate.type,
    placeID = visit.topCandidate.placeID,
    activity_category = NA_character_
  ) |>
  select(
    start_time,
    end_time,
    duration_min,
    date,
    weekday,
    hour,
    record_type,
    transport_mode,
    activity_category,
    placeID,
    lat,
    lon
  ) |>
  filter(!is.na(lat), !is.na(lon)) |>
  arrange(start_time)
```

## Convert Timeline data to spatial format

```{r convert-to-spatial-data}
timeline_sf <- timeline |>
  st_as_sf(coords = c("lon", "lat"), crs = 4326) |>
  st_transform(2056)

coords <- st_coordinates(timeline_sf)

timeline_sf <- timeline_sf |>
  mutate(
    E = coords[, 1],
    N = coords[, 2]
  )
```

## Define activity categories

```{r activity-categories}
activity_categories <- tibble::tribble(
  ~Category, ~Includes,
  "transport", "Train stations, tram stops, bus stops, airports. These are reclassified as transport rather than visit activities.",
  "home", "Residence",
  "education", "University, school",
  "work", "Workplace",
  "shopping", "Supermarket, stores, post office",
  "leisure", "Restaurants, bars, cinema, culture",
  "sport", "Gym, climbing, swimming",
  "nature", "Hikes, parks, mountains",
  "social", "Friends and family",
  "movement", "No POI. Reclassified as movement rather than visit activity.",
  "healthcare", "Doctor, pharmacy",
  "unknown", "Unresolved"
)

activity_categories
#export activity categories
# Export table as CSV
readr::write_csv(
  activity_categories,
  "outputs/activity_categories.csv"
)

```

## Prepare unique visited places

```{r prepare-unique-visits}
visits <- timeline_sf |>
  filter(record_type == "visit") |>
  distinct(placeID, .keep_all = TRUE) |>
  arrange(placeID) |>
  mutate(place_number = row_number())

timeline_sf <- timeline_sf |>
  left_join(
    visits |>
      st_drop_geometry() |>
      select(placeID, place_number),
    by = "placeID"
  )

mapview::mapview(visits)
```

## Add manual activity labels

```{r manual-activity-labels}
manual_place_labels <- tibble(
  place_number = 1:167,
  activity_category = c(
    "shopping", "movement", "leisure", "movement", "work", "transport", "social", "transport",
    "education", "movement", "social", "nature", "sport", "education", "healthcare", "shopping",
    "movement", "education", "leisure", "transport", "leisure", "movement", "movement", "shopping",
    "transport", "shopping", "movement", "movement", "social", "social", "leisure", "movement",
    "transport", "sport", "movement", "transport", "sport", "social", "leisure", "shopping",
    "leisure", "shopping", "leisure", "movement", "leisure", "leisure", "nature", "movement",
    "social", "transport", "movement", "nature", "movement", "movement", "movement", "shopping",
    "education", "nature", "nature", "transport", "social", "nature", "social", "shopping",
    "healthcare", "social", "movement", "sport", "movement", "movement", "transport", "shopping",
    "movement", "movement", "movement", "nature", "social", "leisure", "nature", "social",
    "social", "movement", "shopping", "transport", "movement", "movement", "leisure", "transport",
    "healthcare", "transport", "education", "nature", "shopping", "movement", "transport", "movement",
    "shopping", "education", "education", "transport", "movement", "movement", "social", "leisure",
    "shopping", "shopping", "shopping", "movement", "shopping", "transport", "leisure", "movement",
    "movement", "movement", "social", "movement", "shopping", "shopping", "movement", "transport",
    "shopping", "transport", "leisure", "shopping", "education", "nature", "leisure", "shopping",
    "social", "transport", "transport", "healthcare", "movement", "movement", "transport", "leisure",
    "leisure", "movement", "movement", "leisure", "shopping", "transport", "education", "home",
    "transport", "social", "social", "nature", "movement", "movement", "education", "movement",
    "leisure", "transport", "shopping", "transport", "movement", "movement", "education", "movement",
    "sport", "education", "sport", "sport", "leisure", "nature", "social"
  )
)
visits <- visits |>
  select(-any_of("activity_category")) |>
  left_join(manual_place_labels, by = "place_number") |>
  mutate(
    activity_category = tidyr::replace_na(activity_category, "unknown"),
    activity_category = factor(activity_category, levels = activity_levels)
  )

visits |>
  st_drop_geometry() |>
  count(activity_category, sort = TRUE)
```

## Merge labels back to Timeline data

```{r merge-labels-to-timeline}
timeline_sf <- timeline_sf |>
  left_join(
    visits |>
      st_drop_geometry() |>
      select(placeID, activity_category),
    by = "placeID",
    suffix = c("", "_labelled")
  ) |>
  mutate(
    activity_category = coalesce(
      as.character(activity_category_labelled),
      as.character(activity_category)
    )
  ) |>
  select(-activity_category_labelled)

timeline_sf |>
  filter(record_type == "visit") |>
  count(activity_category, sort = TRUE)

timeline_sf <- timeline_sf |>
  mutate(
    record_type = case_when(
      activity_category %in% c("movement", "transport") ~ activity_category,
      TRUE ~ record_type
    ),
    activity_category = case_when(
      activity_category %in% c("movement", "transport") ~ NA_character_,
      TRUE ~ activity_category
    )
  )

movements <- timeline_sf |>
  filter(record_type == "movement")

visits_labelled <- timeline_sf |>
  filter(record_type == "visit")
```

## Prepare data for the classification model

```{r prepare-model-data}
model_data <- visits_labelled |>
  st_drop_geometry() |>
  filter(!is.na(activity_category)) |>
  mutate(
    activity_category = as.factor(activity_category),
    weekday = as.factor(weekday),
    is_weekend = weekday %in% c("Sat", "Sun")
  ) |>
  select(
    activity_category,
    duration_min,
    weekday,
    hour,
    is_weekend,
    E,
    N
  )

set.seed(123)

train_index <- sample(
  seq_len(nrow(model_data)),
  size = 0.7 * nrow(model_data)
)

train_data <- model_data[train_index, ]
test_data <- model_data[-train_index, ]
```

## Train and evaluate the classification model

```{r train-and-evaluate-model}
activity_model <- multinom(
  activity_category ~ duration_min + weekday + hour + is_weekend + E + N,
  data = train_data,
  trace = FALSE
)

test_predictions <- test_data |>
  mutate(
    predicted_category = predict(activity_model, newdata = test_data)
  )

confusion_matrix <- table(
  Manual = test_predictions$activity_category,
  Predicted = test_predictions$predicted_category
)

confusion_matrix

accuracy <- mean(
  test_predictions$activity_category == test_predictions$predicted_category
)

accuracy
```

## Visualize classification performance

```{r visualize-classification-performance}
p_confusion <- test_predictions |>
  count(activity_category, predicted_category) |>
  ggplot(aes(
    x = activity_category,
    y = predicted_category,
    fill = n
  )) +
  geom_tile(color = "white") +
  geom_text(aes(label = n), color = "black") +
  scale_fill_gradientn(
    colors = c("#f7fbff", "#c6dbef", "#6baed6", "#2171b5", "#08306b")
  ) +
  labs(
    x = "Manual classification",
    y = "Model prediction",
    fill = "Number of visits"
  ) +
  theme_minimal()
p_confusion

ggsave(
  filename = "outputs/plots/p_confusion.png",
  plot = p_confusion,
  width = 8,
  height = 6,
  dpi = 300
)
```

## Apply the model to all labelled visits

```{r predict-all-labelled-visits}
prediction_data <- visits_labelled |>
  st_drop_geometry() |>
  mutate(
    weekday = as.factor(weekday),
    is_weekend = weekday %in% c("Sat", "Sun")
  )

predictions <- predict(
  activity_model,
  newdata = prediction_data
)

visits_labelled_predicted <- visits_labelled |>
  mutate(
    predicted_activity_category = predictions
  )

visits_labelled_predicted |>
  st_drop_geometry() |>
  select(
    placeID,
    start_time,
    activity_category,
    predicted_activity_category
  ) |>
  mutate(
    correct = activity_category == predicted_activity_category
  ) |>
  count(correct)

visits_labelled_predicted_accuracy <- visits_labelled_predicted |>
  st_drop_geometry() |>
  summarise(
    accuracy = mean(activity_category == predicted_activity_category)
  )

visits_labelled_predicted_accuracy
```

## Statistical test against the majority-class baseline

```{r statistical-test}
n_correct <- sum(
  test_predictions$activity_category == test_predictions$predicted_category
)

n_total <- nrow(test_predictions)

class_distribution <- prop.table(table(model_data$activity_category))
class_distribution

baseline <- max(class_distribution)

binom_test_result <- binom.test(
  x = n_correct,
  n = n_total,
  p = baseline
)

binom_test_result
```

## Load isochrones and POI data

```{r load-isochrones-and-poi}
isochrones_15min <- readRDS("outputs/isochrones_15min.rds") |>
  st_make_valid()

pois_by_iso <- readRDS("outputs/pois_by_iso.rds") |>
  st_make_valid() |>
  recode_poi_categories()

isochrones_15min <- isochrones_15min |>
  st_transform(st_crs(visits_labelled))

pois_by_iso <- pois_by_iso |>
  st_transform(st_crs(visits_labelled))

unique(isochrones_15min$mode)
unique(pois_by_iso$mode)
names(pois_by_iso)
```

## Join actual visits with 15-minute accessibility areas

```{r join-visits-with-isochrones}
visits_labelled_iso <- visits_labelled |>
  mutate(
    within_walk_15 = is_within_mode(geometry, isochrones_15min, "Walking"),
    within_bike_15 = is_within_mode(geometry, isochrones_15min, "Cycling"),
    within_pt_15 = is_within_mode(geometry, isochrones_15min, "Public transport proxy")
  )
```

## Compare actual mobility and theoretical accessibility

```{r}
# Actual mobility 

# share of observed visits within 15 min

overall_mobility <- visits_labelled_iso |>
  st_drop_geometry() |>
  filter(
    !is.na(activity_category),
    activity_category != "home"
  ) |>
  summarise(
    n_visits = n(),
    visits_walk_15 = sum(within_walk_15, na.rm = TRUE),
    visits_bike_15 = sum(within_bike_15, na.rm = TRUE),
    share_walk_15 = visits_walk_15 / n_visits * 100,
    share_bike_15 = visits_bike_15 / n_visits * 100
  )

 # By activity type
mobility_table <- visits_labelled_iso |>
  st_drop_geometry() |>
  filter(!is.na(activity_category),
         !activity_category %in% c("home")) |>
  group_by(activity_category) |>
  summarise(
    n_visits = n(),
    visits_walk_15 = sum(within_walk_15, na.rm = TRUE),
    visits_bike_15 = sum(within_bike_15, na.rm = TRUE),
    share_walk_15 = visits_walk_15 / n_visits * 100,
    share_bike_15 = visits_bike_15 / n_visits * 100,
    .groups = "drop"
  )

# Theoretical accessibility: number of POIs inside each isochrone
accessibility_table <- pois_by_iso |>
  st_drop_geometry() |>
  filter(!is.na(poi_activity_category),
         poi_activity_category != "unknown") |>
  group_by(poi_activity_category, mode) |>
  summarise(
    n_accessible_pois = n_distinct(osm_id),
    .groups = "drop"
  ) |>
  pivot_wider(
    names_from = mode,
    values_from = n_accessible_pois,
    values_fill = 0
  ) |>
  rename(
    activity_category = poi_activity_category,
    pois_walk_15 = Walking,
    pois_bike_15 = Cycling
  )

# Combine behavior and accessibility
comparison_table <- mobility_table |>
  left_join(accessibility_table, by = "activity_category") |>
  mutate(
    activity_category = str_to_title(as.character(activity_category))
  )

comparison_table
```

## Visualize activities within 15 minutes

```{r}

Share_within <- tibble(
  Mode = c("Walking", "Cycling"),
  Share = c(
    overall_mobility$share_walk_15,
    overall_mobility$share_bike_15
  )
)


overall_proportion <- ggplot(Share_within, aes(x = Mode, y = Share)) +
  geom_col(width = 0.6) +
  geom_text(
    aes(label = paste0(round(Share, 1), "%")),
    vjust = -0.5
  ) +
  labs(
    x = NULL,
    y = "Activities within 15 minutes (%)",
    title = "Proportion of daily activities within the 15 minutes perimeter"
  ) +
  ylim(0, 100) +
  theme_minimal()

ggsave(
  filename = "outputs/plots/overall_proportion.png",
  plot = overall_proportion,
  width = 12,
  height = 6,
  dpi = 300
)

plot_ready <- comparison_table |>
  transmute(
    Activity = activity_category,
    Walking_POIs = replace_na(pois_walk_15, 0),
    Cycling_POIs = replace_na(pois_bike_15, 0),
    Walking_visits = replace_na(share_walk_15, 0),
    Cycling_visits = replace_na(share_bike_15, 0)
  ) |>
  pivot_longer(
    cols = -Activity,
    names_to = c("mode", "metric"),
    names_sep = "_",
    values_to = "value"
  ) |>
  mutate(
    mode = factor(mode, levels = c("Walking", "Cycling")),
    metric = recode(
      metric,
      POIs = "Accessible POIs\n(absolute number)",
      visits = "Actual visits inside\nisochrone (%)"
    ),
    label = if_else(
      metric == "Accessible POIs\n(absolute number)",
      as.character(round(value, 0)),
      paste0(round(value, 1), "%")
    ),
    Activity = fct_reorder(Activity, value, max)
  )

option_2 <- ggplot( plot_ready,aes(x = value, y = Activity, fill = mode)) +
  geom_col(
    position = position_dodge(width = 0.75),
    width = 0.65
  ) +
  geom_text(
    aes(label = label),
    position = position_dodge(width = 0.75),
    hjust = -0.15,
    size = 3
  ) +
  facet_wrap(
    ~metric,
    scales = "free_x",
    ncol = 2
  ) +
  scale_fill_manual(
    values = c(
      "Walking" = "#E69F00",
      "Cycling" = "#56B4E9"
    )
  ) +
  scale_x_continuous(
    expand = expansion(mult = c(0, 0.18))
  ) +
  coord_cartesian(clip = "off") +
  labs(
    x = NULL,
    y = NULL,
    fill = "Mode"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    strip.text = element_text(face = "bold"),
    panel.grid.major.y = element_blank(),
    plot.margin = margin(5.5, 35, 5.5, 5.5)
  )

option_2

ggsave(
  filename = "outputs/plots/option_2.png",
  plot = option_2,
  width = 12,
  height = 6,
  dpi = 300
)

```

## Visualize activities beyond the 15-minute city

```{r visualize-activities-beyond-15-minutes}
outside_visits <- comparison_table |>
  mutate(
    outside_bike = n_visits - visits_bike_15,
    outside_walk = n_visits - visits_walk_15
  ) |>
  arrange(desc(outside_bike))

p_outside_bike_visits <- ggplot(
  outside_visits,
  aes(
    x = reorder(activity_category, outside_bike),
    y = outside_bike
  )
) +
  geom_col(fill = "grey35") +
  geom_text(
  aes(label = outside_bike),
  hjust = 1.2,
  color = "white",
  size = 3.5
)+
  coord_flip(clip = "off") +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.12))
  ) +
  labs(
    x = NULL,
    y = "Number of visits"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    plot.margin = margin(5.5, 30, 5.5, 5.5)
  )

p_outside_bike_visits
ggsave(
  filename = "outputs/plots/p_outside_bike_visits.png",
  plot = p_outside_bike_visits,
  width = 7,
  height = 6,
  dpi = 300
)

```

## Prepare isochrone and POI subsets

```{r prepare-isochrone-poi-subsets}
create_output_folders()

isochrones_all <- readRDS("outputs/isochrones_15min.rds") |>
  st_make_valid()

pois_by_iso_all <- readRDS("outputs/pois_by_iso.rds") |>
  st_make_valid()

unique(isochrones_all$mode)
unique(pois_by_iso_all$mode)

modes_all <- c("Walking", "Cycling", "E-bike")
modes_sansebike <- c("Walking", "Cycling")

isochrones_all <- isochrones_all |>
  filter(mode %in% modes_all)

isochrones_sansebike <- isochrones_all |>
  filter(mode %in% modes_sansebike)

pois_by_iso_all <- pois_by_iso_all |>
  filter(mode %in% modes_all)

pois_by_iso_sansebike <- pois_by_iso_all |>
  filter(mode %in% modes_sansebike)

pois_unique_all <- deduplicate_pois(pois_by_iso_all)
pois_unique_sansebike <- deduplicate_pois(pois_by_iso_sansebike)
```

## Recode and save POI subsets

```{r recode-and-save-poi-subsets}
pois_by_iso_all <- recode_poi_categories(pois_by_iso_all)
pois_by_iso_sansebike <- recode_poi_categories(pois_by_iso_sansebike)
pois_unique_all <- recode_poi_categories(pois_unique_all)
pois_unique_sansebike <- recode_poi_categories(pois_unique_sansebike)

saveRDS(isochrones_all, "outputs/isochrones_all/isochrones_all.rds")
saveRDS(isochrones_sansebike, "outputs/isochrones_sansebike/isochrones_sansebike.rds")
saveRDS(pois_by_iso_all, "outputs/pois_all/pois_by_iso_all.rds")
saveRDS(pois_by_iso_sansebike, "outputs/pois_sansebike/pois_by_iso_sansebike.rds")
saveRDS(pois_unique_all, "outputs/pois_all/pois_unique_all.rds")
saveRDS(pois_unique_sansebike, "outputs/pois_sansebike/pois_unique_sansebike.rds")

isochrones_all |>
  st_drop_geometry() |>
  count(mode)

isochrones_sansebike |>
  st_drop_geometry() |>
  count(mode)

pois_by_iso_all |>
  st_drop_geometry() |>
  count(mode, poi_category_original, poi_activity_category, sort = TRUE)

pois_by_iso_sansebike |>
  st_drop_geometry() |>
  count(mode, poi_category_original, poi_activity_category, sort = TRUE)
```

## Prepare data for map visualisations

```{r prepare-map-data}
isochrones_all <- st_transform(isochrones_all, 4326)
isochrones_sansebike <- st_transform(isochrones_sansebike, 4326)

pois_unique_all <- st_transform(pois_unique_all, 4326)
pois_unique_sansebike <- st_transform(pois_unique_sansebike, 4326)

home_sf <- st_transform(home_sf, 4326)

pois_unique_all$poi_activity_category <- as.factor(pois_unique_all$poi_activity_category)
pois_unique_sansebike$poi_activity_category <- as.factor(pois_unique_sansebike$poi_activity_category)

set.seed(123)

poi_levels <- levels(pois_unique_all$poi_activity_category)
poi_colors <- sample(grDevices::rainbow(length(poi_levels), s = 0.8, v = 0.9))
names(poi_colors) <- poi_levels
```


## Static map without E-bike

```{r static-map-without-ebike}
iso_sansebike_2056 <- isochrones_sansebike |>
  st_transform(2056)

pois_sansebike_2056 <- pois_unique_sansebike |>
  st_transform(2056)

home_2056 <- home_sf |>
  st_transform(2056)

map_pois_sansebike_black <- ggplot() +
  geom_sf(
    data = iso_sansebike_2056,
    fill = NA,
    color = NA
  ) +
  geom_sf(
    data = iso_sansebike_2056 |> filter(mode == "Cycling"),
    aes(fill = "Cycling isochrone"),
    color = "darkgreen",
    alpha = 0.22,
    linewidth = 1
  ) +
  geom_sf(
    data = iso_sansebike_2056 |> filter(mode == "Walking"),
    aes(fill = "Walking isochrone"),
    color = "darkorange",
    alpha = 0.35,
    linewidth = 1
  ) +
  geom_sf(
    data = pois_sansebike_2056,
    aes(color = poi_activity_category),
    size = 1.6,
    alpha = 0.9
  ) +
  geom_sf(
    data = home_2056,
    aes(shape = "Home"),
    color = "red",
    size = 3
  ) +
  scale_fill_manual(
    name = "Isochrones",
    values = c(
      "Cycling isochrone" = "lightgreen",
      "Walking isochrone" = "orange"
    )
  ) +
  scale_shape_manual(
    name = NULL,
    values = c("Home" = 16)
  ) +
  labs(
    title = NULL,
    subtitle = NULL,
    color = "POI category"
  ) +
  theme_void() +
  theme(
    plot.background = element_rect(fill = "black", color = NA),
    panel.background = element_rect(fill = "black", color = NA),
    legend.background = element_rect(fill = "black", color = NA),
    legend.key = element_rect(fill = "black", color = NA),
    legend.text = element_text(color = "white"),
    legend.title = element_text(color = "white"),
    plot.subtitle = element_text(color = "white")
  )

map_pois_sansebike_black

ggsave(
  filename = "outputs/plots/map_pois_sansebike_black.png",
  plot = map_pois_sansebike_black,
  width = 12,
  height = 6,
  dpi = 300
)

```





