---
title: "Data_preprocessing"
format: html
---

```{r}
library(jsonlite)
library(tidyverse)
library(lubridate)
library(sf)
library(ggplot2)
library(tmap)
library(leaflet)
library(mapview)
```

## Importing the google timeline

```{r}

timeline_raw <- fromJSON("timeline.json", flatten = TRUE)

names(timeline_raw)
glimpse(timeline_raw)



```

## Cleaning of the dataset, keep only relevant

```{r}
#convert timestamps into movement data. 

timeline <- timeline_raw |>
  mutate(
    start_time = ymd_hms(startTime),
    end_time = ymd_hms(endTime),
    duration_min = as.numeric(difftime(end_time, start_time, units = "mins")),
    date = as_date(start_time),
    weekday = wday(start_time, label = TRUE, week_start = 1),
    hour = hour(startTime),

    record_type = case_when(
      !is.na(activity.distanceMeters) ~ "movement",
      !is.na(visit.probability) ~ "visit",
      TRUE ~ "unknown"
    ),

    location = case_when(
      record_type == "movement" ~ activity.start,
      record_type == "visit" ~ visit.topCandidate.placeLocation
    ),

    lat = as.numeric(str_extract(location, "(?<=geo:)[0-9.\\-]+")),
    lon = as.numeric(str_extract(location, "(?<=,)[0-9.\\-]+")),

    transport_mode = activity.topCandidate.type,
    placeID = visit.topCandidate.placeID,
    activity_category = NA_character_
  ) |>
  select(start_time, end_time, duration_min, date, weekday,
         record_type, transport_mode, activity_category,
         placeID, lat, lon) |>
  filter(!is.na(lat), !is.na(lon)) |>
  arrange(start_time)


```

## convert to spatial object 

```{r}
#Convert table into Spatial object

timeline_sf <- timeline |>
  st_as_sf(coords = c("lon", "lat"), crs = 4326) |>
  st_transform(2056)

# separate coordinates in 2 columns like the Sabi example.
coords <- st_coordinates(timeline_sf)

timeline_sf <- timeline_sf |>
  mutate(
    E = coords[, 1],
    N = coords[, 2]
  )
```

## Semantic Annotation of Activity categories

### Semantic annotation categories
```{r}
activity_categories <- tibble::tribble(
  ~category, ~includes,

  "transport", "Train stations, tram stops, bus stops, airports - probably to be filtered out",
  "home", "Residence",
  "education", "University, school",
  "work", "Workplace",
  "shopping", "Supermarket, stores, post office",
  "leisure", "Restaurants, bars, cinema, culture",
  "sport", "Gym, climbing, swimming",
  "nature", "Hikes, parks, mountains",
  "social", "Friends/family",
  "movement", "No POI (reclassify to movement as record type instead of visit)",
  "healthcare", "Doctor, pharmacy",
  "unknown", "Unresolved"
)

activity_categories
```


```{r}
#creates one row per unique visited place
visits <- timeline_sf |>
  filter(record_type == "visit") |>
  distinct(placeID, .keep_all = TRUE) |>
  arrange(placeID) |>
  mutate(
    place_number = row_number()
  )
timeline_sf <- timeline_sf |>
  left_join(
    visits |>
      st_drop_geometry() |>
      select(placeID, place_number),
    by = "placeID"
  )

mapview::mapview(visits)

# manual labelling 
visits <- visits |>
  mutate(
    activity_category = case_when(
      place_number == 1 ~ "shopping",
      place_number == 2 ~ "movement",
      place_number == 3 ~ "leisure",
      place_number == 4 ~ "movement",
      place_number == 5 ~ "work",
      place_number == 6 ~ "transport",
      place_number == 7 ~ "social",
      place_number == 8 ~ "transport",
      place_number == 9 ~ "education",
      place_number == 10 ~ "movement",
      place_number == 11 ~ "social",
      place_number == 12 ~ "nature",
      place_number == 13 ~ "sport",
      place_number == 14 ~ "education",
      place_number == 15 ~ "healthcare",
      place_number == 16 ~ "shopping",
      place_number == 17 ~ "movement",
      place_number == 18 ~ "education",
      place_number == 19 ~ "leisure",
      place_number == 20 ~ "transport",
      place_number == 21 ~ "leisure",
      place_number == 22 ~ "movement",
      place_number == 23 ~ "movement",
      place_number == 24 ~ "shopping",
      place_number == 25 ~ "transport",
      place_number == 26 ~ "shopping",
      place_number == 27 ~ "movement",
      place_number == 28 ~ "movement",
      place_number == 29 ~ "social",
      place_number == 30 ~ "social",
      place_number == 31 ~ "leisure",
      place_number == 32 ~ "movement",
      place_number == 33 ~ "transport",
      place_number == 34 ~ "sport",
      place_number == 35 ~ "movement",
      place_number == 36 ~ "transport",
      place_number == 37 ~ "sport",
      place_number == 38 ~ "social",
      place_number == 39 ~ "leisure",
      place_number == 40 ~ "shopping",
      place_number == 41 ~ "leisure",
      place_number == 42 ~ "shopping",
      place_number == 43 ~ "leisure",
      place_number == 44 ~ "movement",
      place_number == 45 ~ "leisure",
      place_number == 46 ~ "leisure",
      place_number == 47 ~ "nature",
      place_number == 48 ~ "movement",
      place_number == 49 ~ "social",
      place_number == 50 ~ "transport",
      place_number == 51 ~ "movement",
      place_number == 52 ~ "nature",
      place_number == 53 ~ "movement",
      place_number == 54 ~ "movement",
      place_number == 55 ~ "movement",
      place_number == 56 ~ "shopping",
      place_number == 57 ~ "education",
      place_number == 58 ~ "nature",
      place_number == 59 ~ "nature",
      place_number == 60 ~ "transport",
      place_number == 61 ~ "social",
      place_number == 62 ~ "nature",
      place_number == 63 ~ "social",
      place_number == 64 ~ "shopping",
      place_number == 65 ~ "healthcare",
      place_number == 66 ~ "social",
      place_number == 67 ~ "movement",
      place_number == 68 ~ "sport",
      place_number == 69 ~ "movement",
      place_number == 70 ~ "movement",
      place_number == 71 ~ "transport",
      place_number == 72 ~ "shopping",
      place_number == 73 ~ "movement",
      place_number == 74 ~ "movement",
      place_number == 75 ~ "movement",
      place_number == 76 ~ "nature",
      place_number == 77 ~ "social",
      place_number == 78 ~ "leisure",
      place_number == 79 ~ "nature",
      place_number == 80 ~ "social",
      place_number == 81 ~ "social",
      place_number == 82 ~ "movement",
      place_number == 83 ~ "shopping",
      place_number == 84 ~ "transport",
      place_number == 85 ~ "movement",
      place_number == 86 ~ "movement",
      place_number == 87 ~ "leisure",
      place_number == 88 ~ "transport",
      place_number == 89 ~ "healthcare",
      place_number == 90 ~ "transport",
      place_number == 91 ~ "education",
      place_number == 92 ~ "nature",
      place_number == 93 ~ "shopping",
      place_number == 94 ~ "movement",
      place_number == 95 ~ "transport",
      place_number == 96 ~ "movement",
      place_number == 97 ~ "shopping",
      place_number == 98 ~ "education",
      place_number == 99 ~ "education",
      place_number == 100 ~ "transport",
      place_number == 101 ~ "movement",
      place_number == 102 ~ "movement",
      place_number == 103 ~ "social",
      place_number == 104 ~ "leisure",
      place_number == 105 ~ "shopping",
      place_number == 106 ~ "shopping",
      place_number == 107 ~ "shopping",
      place_number == 108 ~ "movement",
      place_number == 109 ~ "shopping",
      place_number == 110 ~ "transport",
      place_number == 111 ~ "leisure",
      place_number == 112 ~ "movement",
      place_number == 113 ~ "movement",
      place_number == 114 ~ "movement",
      place_number == 115 ~ "social",
      place_number == 116 ~ "movement",
      place_number == 117 ~ "shopping",
      place_number == 118 ~ "shopping",
      place_number == 119 ~ "movement",
      place_number == 120 ~ "transport",
      place_number == 121 ~ "shopping",
      place_number == 122 ~ "transport",
      place_number == 123 ~ "leisure",
      place_number == 124 ~ "shopping",
      place_number == 125 ~ "education",
      place_number == 126 ~ "nature",
      place_number == 127 ~ "leisure",
      place_number == 128 ~ "shopping",
      place_number == 129 ~ "social",
      place_number == 130 ~ "transport",
      place_number == 131 ~ "transport",
      place_number == 132 ~ "healthcare",
      place_number == 133 ~ "movement",
      place_number == 134 ~ "movement",
      place_number == 135 ~ "transport",
      place_number == 136 ~ "leisure",
      place_number == 137 ~ "leisure",
      place_number == 138 ~ "movement",
      place_number == 139 ~ "movement",
      place_number == 140 ~ "leisure",
      place_number == 141 ~ "shopping",
      place_number == 142 ~ "transport",
      place_number == 143 ~ "education",
      place_number == 144 ~ "home",
      place_number == 145 ~ "transport",
      place_number == 146 ~ "social",
      place_number == 147 ~ "social",
      place_number == 148 ~ "nature",
      place_number == 149 ~ "movement",
      place_number == 150 ~ "movement",
      place_number == 151 ~ "education",
      place_number == 152 ~ "movement",
      place_number == 153 ~ "leisure",
      place_number == 154 ~ "transport",
      place_number == 155 ~ "shopping",
      place_number == 156 ~ "transport",
      place_number == 157 ~ "movement",
      place_number == 158 ~ "movement",
      place_number == 159 ~ "education",
      place_number == 160 ~ "movement",
      place_number == 161 ~ "sport",
      place_number == 162 ~ "education",
      place_number == 163 ~ "sport",
      place_number == 164 ~ "sport",
      place_number == 165 ~ "leisure",
      place_number == 166 ~ "nature",
      place_number == 167 ~ "social",
      TRUE ~ "unknown"
    )
  )


```

## Merging the labelling to the dataset

```{r}
timeline_sf <- timeline_sf |>
  left_join(
    visits |>
      st_drop_geometry() |>
      select(placeID, activity_category),
    by = "placeID",
    suffix = c("", "_labelled")
  ) |>
  mutate(
    activity_category = coalesce(activity_category_labelled, activity_category)
  ) |>
  select(-activity_category_labelled)

timeline_sf |>
  filter(record_type == "visit") |>
  count(activity_category, sort = TRUE)

# si category_type movement, reclassify in record type 
timeline_sf <- timeline_sf |>
  mutate(
    record_type = case_when(
      activity_category == "movement" ~ "movement",
      TRUE ~ record_type
    ),
    activity_category = case_when(
      activity_category == "movement" ~ NA_character_,
      TRUE ~ activity_category
    )
  )

movements <- timeline_sf |> filter(record_type == "movement")
visits_labelled <- timeline_sf |> filter(record_type == "visit")



```


## Visualize

```{r}
# Visits by activity category
tm_shape(visits_labelled) +
  tm_dots(
    col = "activity_category",
    size = 1,
    palette = "Set2",
    title = "Activity category"
  ) +
  tm_layout(
    title = "Visited places by activity category"
  )
tmap_mode("view")


# Unique visited places, sized by frequency
visit_frequency <- visits_labelled |>
  st_drop_geometry() |>
  count(placeID, activity_category, sort = TRUE)

visit_points <- visits_labelled |>
  distinct(placeID, .keep_all = TRUE) |>
  left_join(visit_frequency, by = c("placeID", "activity_category"))

tm_shape(visit_points) +
  tm_dots(
    col = "activity_category",
    size = "n",
    palette = "Set2",
    title.col = "Activity category",
    title.size = "Number of visits"
  ) +
  tm_layout(
    title = "Most frequently visited places"
  )

# Movements by transport mode

tm_shape(movements) +
  tm_dots(
    col = "transport_mode",
    size = 0.8,
    palette = "Dark2",
    title = "Transport mode"
  ) +
  tm_layout(
    title = "Movement points by transport mode"
  )

```
## Activity shape per activity category

```{r}

# for one category
category <- "education"

activity_space_cat <- timeline_sf |>
  filter(record_type == "visit") |>
  filter(activity_category == category) |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_space_cat) +
  tm_polygons(alpha = 0.4) +
tm_shape(
  timeline_sf |>
    filter(activity_category == category)
) +
  tm_dots(size = 0.05)

# for all categories
activity_spaces <- timeline_sf |>
  filter(record_type == "visit") |>
  filter(!is.na(activity_category)) |>
  group_by(activity_category) |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_spaces) +
  tm_polygons(
    col = "activity_category",
    alpha = 0.4
  ) +
tm_shape(
  timeline_sf |>
    filter(record_type == "visit")
) +
  tm_dots(
    col = "activity_category",
    size = 0.05
  )

# full activity space
activity_space_full <- timeline_sf |>
  filter(record_type == "visit") |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_space_full) +
  tm_polygons(
    alpha = 0.3
  ) +
tm_shape(
  timeline_sf |>
    filter(record_type == "visit")
) +
  tm_dots(size = 0.03)

```
## integration of isochrones

```{r}
#load the saved objects 
isochrones_15min <- readRDS("outputs/isochrones_15min.rds")
pois_by_iso <- readRDS("outputs/pois_by_iso.rds")

#Make sure CRS match
isochrones_15min <- st_transform(
  isochrones_15min,
  st_crs(visits_labelled)
)

# join isochrones to visited places
visits_labelled_iso <- visits_labelled |>
  mutate(
    within_walk_15 =
      lengths(st_within(
        geometry,
        isochrones_15min[isochrones_15min$mode == "Walking", ]
      )) > 0,

    within_bike_15 =
      lengths(st_within(
        geometry,
        isochrones_15min[isochrones_15min$mode == "Cycling", ]
      )) > 0,

    within_pt_15 =
      lengths(st_within(
        geometry,
        isochrones_15min[isochrones_15min$mode == "Public transport proxy", ]
      )) > 0
  )


```
## match activity category of point of interest with activity categories of mobility data. 

```{r}
category_crosswalk <- tibble(
  activity_category = c(
    "shopping",
    "nature",
    "healthcare",
    "leisure",
    "sport",
    "education",
    "work"
  ),
  poi_category = c(
    "Groceries",
    "Park / forest",
    "Pharmacy / doctor",
    "Restaurants",
    "Sport",
    "University",
    "Work"
  )
)


```



## Results

```{r}
# practice
mobility_table <- visits_labelled_iso |>
  st_drop_geometry() |>
  filter(activity_category != "home") |>
  group_by(activity_category) |>
  summarise(
    n_visits = n(),
    within_walk_15 = sum(within_walk_15, na.rm = TRUE),
    within_bike_15 = sum(within_bike_15, na.rm = TRUE),
    within_pt_15 = sum(within_pt_15, na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(
    share_walk_15 = round(within_walk_15 / n_visits * 100, 1),
    share_bike_15 = round(within_bike_15 / n_visits * 100, 1),
    share_pt_15 = round(within_pt_15 / n_visits * 100, 1)
  ) |>
  arrange(desc(n_visits))

#in theory
accessibility_table <- pois_by_iso |>
  st_drop_geometry() |>
  group_by(poi_category) |>
  summarise(
    n_pois = n(),

    within_walk_15 = sum(mode == "Walking"),
    within_bike_15 = sum(mode == "Cycling"),
    within_pt_15 = sum(mode == "Public transport proxy"),

    .groups = "drop"
  ) |>
  mutate(
    share_walk_15 = round(within_walk_15 / n_pois * 100, 1),
    share_bike_15 = round(within_bike_15 / n_pois * 100, 1),
    share_pt_15 = round(within_pt_15 / n_pois * 100, 1)
  )

names(pois_by_iso)

# match the categories
comparison_table <- mobility_table |>
  left_join(
    category_crosswalk,
    by = "activity_category"
  ) |>
  left_join(
    accessibility_table,
    by = "poi_category",
    suffix = c("_mobility", "_theory")
  )
```

## Join the actual mobility and theoretical accessibility
```{r}
summary_table <- mobility_table |>
  left_join(
    category_crosswalk,
    by = "activity_category"
  ) |>
  left_join(
    accessibility_table,
    by = "poi_category",
    suffix = c("_mobility", "_theory")
  ) |>
  transmute(
    Activity = activity_category,
    Visits = n_visits,

    `Walk (%)` = share_walk_15_mobility,
    `Walk Opportunities` = within_walk_15_theory,

    `Bike (%)` = share_bike_15_mobility,
    `Bike Opportunities` = within_bike_15_theory,

    `PT (%)` = share_pt_15_mobility,
    `PT Opportunities` = within_pt_15_theory
  )
```

## Visualisation 

### What proportion of activities occur within 15 minutes?

```{r}


rq1_data <- summary_table |>
  select(Activity, `Walk (%)`, `Bike (%)`, `PT (%)`) |>
  pivot_longer(
    -Activity,
    names_to = "Mode",
    values_to = "Share"
  )
# as a frouped bar chart
ggplot(rq1_data,
       aes(x = reorder(Activity, -Share),
           y = Share,
           fill = Mode)) +
  geom_col(position = "dodge") +
  labs(
    x = "",
    y = "% of visits within 15 minutes",
    fill = "Transport mode"
  ) +
  theme_minimal() +
  coord_flip()

```

### Accessibility Gap
```{r}

access_gap_data <- summary_table |>
  filter(!Activity %in% c("transport", "social")) |>
  mutate(
    `Walk opportunity share (%)` =
      `Walk Opportunities` / sum(`Walk Opportunities`, na.rm = TRUE) * 100,
    `Bike opportunity share (%)` =
      `Bike Opportunities` / sum(`Bike Opportunities`, na.rm = TRUE) * 100,
    `PT opportunity share (%)` =
      `PT Opportunities` / sum(`PT Opportunities`, na.rm = TRUE) * 100
  )

bike_gap <- access_gap_data |>
  transmute(
    Activity,
    `Observed visits within 15 min (%)` = `Bike (%)`,
    `Share of bike-accessible opportunities (%)` = `Bike opportunity share (%)`
  ) |>
  pivot_longer(
    -Activity,
    names_to = "Measure",
    values_to = "Value"
  )

ggplot(
  bike_gap,
  aes(
    x = reorder(Activity, Value),
    y = Value,
    fill = Measure
  )
) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(
    title = "Observed use versus theoretical accessibility by bike",
    subtitle = "Comparison between actual visits within 15 minutes and nearby opportunities",
    x = "",
    y = "%",
    fill = ""
  ) +
  theme_minimal()
```

### Activities occurring beyond the 15-minute city 

only the cycling isochrone was used here
```{r}
#considering the absolute frequency of visits 
outside_visits <- summary_table |>
  mutate(
    outside_bike = round(Visits * (100 - `Bike (%)`) / 100)
  ) |>
  arrange(desc(outside_bike))

ggplot(outside_visits,
       aes(reorder(Activity, outside_bike),
           outside_bike)) +
  geom_col() +
  coord_flip()

# considering relative frequency.( invert from research question 1)
figure3_bike <- summary_table |>
  filter(!Activity %in% c("transport")) |>
  mutate(
    Beyond_15min = 100 - `Bike (%)`
  ) |>
  arrange(desc(Beyond_15min))

ggplot(
  figure3_bike,
  aes(
    x = reorder(Activity, Beyond_15min),
    y = Beyond_15min
  )
) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Activities occurring beyond 15 minutes by bike",
    x = "",
    y = "% of visits beyond 15 minutes"
  ) +
  theme_minimal()

```

