---
title: "datapreprocessing clean"
author: "Lucie Kern and Noémie Simon"
format: html
---
---
title: "Data preprocessing and accessibility analysis"
format: html
---

## Load libraries and settings

```{r setup, message=FALSE, warning=FALSE}
library(jsonlite)
library(tidyverse)
library(lubridate)
library(sf)
library(tmap)
library(mapview)
library(nnet)
library(ggplot2)

knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)

tmap_mode("view")
```

## Define helper functions and constants

```{r helper-functions}
activity_levels <- c(
  "shopping",
  "nature",
  "healthcare",
  "leisure",
  "sport",
  "education",
  "work",
  "social",
  "home",
  "movement",
  "transport",
  "unknown"
)

analysis_activity_levels <- c(
  "shopping",
  "nature",
  "healthcare",
  "leisure",
  "sport",
  "education",
  "work"
)

home_sf <- st_sf(
  geometry = st_sfc(st_point(c(8.546069, 47.409620))),
  crs = 4326
)

create_output_folders <- function() {
  dir.create("outputs/isochrones_all", recursive = TRUE, showWarnings = FALSE)
  dir.create("outputs/isochrones_sansebike", recursive = TRUE, showWarnings = FALSE)
  dir.create("outputs/pois_all", recursive = TRUE, showWarnings = FALSE)
  dir.create("outputs/pois_sansebike", recursive = TRUE, showWarnings = FALSE)
}

deduplicate_pois <- function(x) {
  dedup_cols <- intersect(
    c("osm_id", "name", "poi_category", "poi_subcategory"),
    names(x)
  )
  
  if (length(dedup_cols) == 0) {
    return(x)
  }
  
  x |>
    distinct(across(all_of(dedup_cols)), .keep_all = TRUE)
}

recode_poi_categories <- function(x) {
  if (!"poi_category_original" %in% names(x)) {
    x <- x |>
      mutate(poi_category_original = poi_category)
  }
  
  x |>
    mutate(
      poi_activity_category = case_when(
        poi_category %in% c("Groceries") ~ "shopping",
        poi_category %in% c("Park / forest") ~ "nature",
        poi_category %in% c("Pharmacy / doctor", "Pharmacy / doctor / doctors") ~ "healthcare",
        poi_category %in% c("Restaurants") ~ "leisure",
        poi_category %in% c("Sport") ~ "sport",
        poi_category %in% c("University") ~ "education",
        poi_category %in% c("Work") ~ "work",
        TRUE ~ "unknown"
      ),
      poi_activity_category = factor(
        poi_activity_category,
        levels = c(analysis_activity_levels, "unknown")
      )
    )
}

is_within_mode <- function(points, polygons, mode_name) {
  polygons_mode <- polygons |>
    filter(mode == mode_name)
  
  lengths(st_within(points, polygons_mode)) > 0
}
```

## Load Google Timeline data

```{r load-google-timeline}
timeline_raw <- fromJSON("timeline.json", flatten = TRUE)

names(timeline_raw)
glimpse(timeline_raw)
```

## Clean Timeline data

```{r clean-timeline-data}
timeline <- timeline_raw |>
  mutate(
    start_time = ymd_hms(startTime),
    end_time = ymd_hms(endTime),
    duration_min = as.numeric(difftime(end_time, start_time, units = "mins")),
    date = as_date(start_time),
    weekday = wday(start_time, label = TRUE, week_start = 1),
    hour = hour(start_time),
    record_type = case_when(
      !is.na(activity.distanceMeters) ~ "movement",
      !is.na(visit.probability) ~ "visit",
      TRUE ~ "unknown"
    ),
    location = case_when(
      record_type == "movement" ~ activity.start,
      record_type == "visit" ~ visit.topCandidate.placeLocation,
      TRUE ~ NA_character_
    ),
    lat = as.numeric(str_extract(location, "(?<=geo:)[0-9.-]+")),
    lon = as.numeric(str_extract(location, "(?<=,)[0-9.-]+")),
    transport_mode = activity.topCandidate.type,
    placeID = visit.topCandidate.placeID,
    activity_category = NA_character_
  ) |>
  select(
    start_time,
    end_time,
    duration_min,
    date,
    weekday,
    hour,
    record_type,
    transport_mode,
    activity_category,
    placeID,
    lat,
    lon
  ) |>
  filter(!is.na(lat), !is.na(lon)) |>
  arrange(start_time)
```

## Convert Timeline data to spatial format

```{r convert-to-spatial-data}
timeline_sf <- timeline |>
  st_as_sf(coords = c("lon", "lat"), crs = 4326) |>
  st_transform(2056)

coords <- st_coordinates(timeline_sf)

timeline_sf <- timeline_sf |>
  mutate(
    E = coords[, 1],
    N = coords[, 2]
  )
```

## Define activity categories

```{r activity-categories}
activity_categories <- tibble::tribble(
  ~category, ~includes,
  "transport", "Train stations, tram stops, bus stops, airports. These are reclassified as transport rather than visit activities.",
  "home", "Residence",
  "education", "University, school",
  "work", "Workplace",
  "shopping", "Supermarket, stores, post office",
  "leisure", "Restaurants, bars, cinema, culture",
  "sport", "Gym, climbing, swimming",
  "nature", "Hikes, parks, mountains",
  "social", "Friends and family",
  "movement", "No POI. Reclassified as movement rather than visit activity.",
  "healthcare", "Doctor, pharmacy",
  "unknown", "Unresolved"
)

activity_categories
```

## Prepare unique visited places

```{r prepare-unique-visits}
visits <- timeline_sf |>
  filter(record_type == "visit") |>
  distinct(placeID, .keep_all = TRUE) |>
  arrange(placeID) |>
  mutate(place_number = row_number())

timeline_sf <- timeline_sf |>
  left_join(
    visits |>
      st_drop_geometry() |>
      select(placeID, place_number),
    by = "placeID"
  )

mapview::mapview(visits)
```

## Add manual activity labels

```{r manual-activity-labels}
manual_place_labels <- tibble(
  place_number = 1:167,
  activity_category = c(
    "shopping", "movement", "leisure", "movement", "work", "transport", "social", "transport",
    "education", "movement", "social", "nature", "sport", "education", "healthcare", "shopping",
    "movement", "education", "leisure", "transport", "leisure", "movement", "movement", "shopping",
    "transport", "shopping", "movement", "movement", "social", "social", "leisure", "movement",
    "transport", "sport", "movement", "transport", "sport", "social", "leisure", "shopping",
    "leisure", "shopping", "leisure", "movement", "leisure", "leisure", "nature", "movement",
    "social", "transport", "movement", "nature", "movement", "movement", "movement", "shopping",
    "education", "nature", "nature", "transport", "social", "nature", "social", "shopping",
    "healthcare", "social", "movement", "sport", "movement", "movement", "transport", "shopping",
    "movement", "movement", "movement", "nature", "social", "leisure", "nature", "social",
    "social", "movement", "shopping", "transport", "movement", "movement", "leisure", "transport",
    "healthcare", "transport", "education", "nature", "shopping", "movement", "transport", "movement",
    "shopping", "education", "education", "transport", "movement", "movement", "social", "leisure",
    "shopping", "shopping", "shopping", "movement", "shopping", "transport", "leisure", "movement",
    "movement", "movement", "social", "movement", "shopping", "shopping", "movement", "transport",
    "shopping", "transport", "leisure", "shopping", "education", "nature", "leisure", "shopping",
    "social", "transport", "transport", "healthcare", "movement", "movement", "transport", "leisure",
    "leisure", "movement", "movement", "leisure", "shopping", "transport", "education", "home",
    "transport", "social", "social", "nature", "movement", "movement", "education", "movement",
    "leisure", "transport", "shopping", "transport", "movement", "movement", "education", "movement",
    "sport", "education", "sport", "sport", "leisure", "nature", "social"
  )
)
visits <- visits |>
  select(-any_of("activity_category")) |>
  left_join(manual_place_labels, by = "place_number") |>
  mutate(
    activity_category = tidyr::replace_na(activity_category, "unknown"),
    activity_category = factor(activity_category, levels = activity_levels)
  )

visits |>
  st_drop_geometry() |>
  count(activity_category, sort = TRUE)
```

## Merge labels back to Timeline data

```{r merge-labels-to-timeline}
timeline_sf <- timeline_sf |>
  left_join(
    visits |>
      st_drop_geometry() |>
      select(placeID, activity_category),
    by = "placeID",
    suffix = c("", "_labelled")
  ) |>
  mutate(
    activity_category = coalesce(
      as.character(activity_category_labelled),
      as.character(activity_category)
    )
  ) |>
  select(-activity_category_labelled)

timeline_sf |>
  filter(record_type == "visit") |>
  count(activity_category, sort = TRUE)

timeline_sf <- timeline_sf |>
  mutate(
    record_type = case_when(
      activity_category %in% c("movement", "transport") ~ activity_category,
      TRUE ~ record_type
    ),
    activity_category = case_when(
      activity_category %in% c("movement", "transport") ~ NA_character_,
      TRUE ~ activity_category
    )
  )

movements <- timeline_sf |>
  filter(record_type == "movement")

visits_labelled <- timeline_sf |>
  filter(record_type == "visit")
```

## Prepare data for the classification model

```{r prepare-model-data}
model_data <- visits_labelled |>
  st_drop_geometry() |>
  filter(!is.na(activity_category)) |>
  mutate(
    activity_category = as.factor(activity_category),
    weekday = as.factor(weekday),
    is_weekend = weekday %in% c("Sat", "Sun")
  ) |>
  select(
    activity_category,
    duration_min,
    weekday,
    hour,
    is_weekend,
    E,
    N
  )

set.seed(123)

train_index <- sample(
  seq_len(nrow(model_data)),
  size = 0.7 * nrow(model_data)
)

train_data <- model_data[train_index, ]
test_data <- model_data[-train_index, ]
```

## Train and evaluate the classification model

```{r train-and-evaluate-model}
activity_model <- multinom(
  activity_category ~ duration_min + weekday + hour + is_weekend + E + N,
  data = train_data,
  trace = FALSE
)

test_predictions <- test_data |>
  mutate(
    predicted_category = predict(activity_model, newdata = test_data)
  )

confusion_matrix <- table(
  Manual = test_predictions$activity_category,
  Predicted = test_predictions$predicted_category
)

confusion_matrix

accuracy <- mean(
  test_predictions$activity_category == test_predictions$predicted_category
)

accuracy
```

## Visualize classification performance

```{r visualize-classification-performance}
test_predictions |>
  count(activity_category, predicted_category) |>
  ggplot(aes(
    x = activity_category,
    y = predicted_category,
    fill = n
  )) +
  geom_tile() +
  geom_text(aes(label = n)) +
  labs(
    title = "Manual vs predicted activity classification",
    x = "Manual classification",
    y = "Model prediction",
    fill = "Number of visits"
  ) +
  theme_minimal()
```

## Apply the model to all labelled visits

```{r predict-all-labelled-visits}
prediction_data <- visits_labelled |>
  st_drop_geometry() |>
  mutate(
    weekday = as.factor(weekday),
    is_weekend = weekday %in% c("Sat", "Sun")
  )

predictions <- predict(
  activity_model,
  newdata = prediction_data
)

visits_labelled_predicted <- visits_labelled |>
  mutate(
    predicted_activity_category = predictions
  )

visits_labelled_predicted |>
  st_drop_geometry() |>
  select(
    placeID,
    start_time,
    activity_category,
    predicted_activity_category
  ) |>
  mutate(
    correct = activity_category == predicted_activity_category
  ) |>
  count(correct)

visits_labelled_predicted_accuracy <- visits_labelled_predicted |>
  st_drop_geometry() |>
  summarise(
    accuracy = mean(activity_category == predicted_activity_category)
  )

visits_labelled_predicted_accuracy
```

## Statistical test against the majority-class baseline

```{r statistical-test}
n_correct <- sum(
  test_predictions$activity_category == test_predictions$predicted_category
)

n_total <- nrow(test_predictions)

class_distribution <- prop.table(table(model_data$activity_category))
class_distribution

baseline <- max(class_distribution)

binom_test_result <- binom.test(
  x = n_correct,
  n = n_total,
  p = baseline
)

binom_test_result
```

To evaluate the predictive performance of the activity classification model, a hold-out test dataset containing `r n_total` observations was used. The model correctly classified `r n_correct` observations, resulting in an overall accuracy of `r scales::percent(accuracy, accuracy = 0.1)`.

As a baseline, the majority-class classifier was considered. A naive classifier assigning every observation to the largest activity category would achieve an accuracy of `r scales::percent(baseline, accuracy = 0.1)`.

An exact binomial test was conducted to assess whether the observed accuracy differed from the majority-class baseline. The estimated accuracy was `r scales::percent(binom_test_result$estimate, accuracy = 0.1)`, with a 95% confidence interval ranging from `r scales::percent(binom_test_result$conf.int[1], accuracy = 0.1)` to `r scales::percent(binom_test_result$conf.int[2], accuracy = 0.1)`.

These results suggest that the model captures meaningful spatial and temporal patterns associated with different activity types and performs better than a naive classification strategy.

## Visualize labelled mobility data

```{r visualize-labelled-mobility}
tm_shape(visits_labelled) +
  tm_dots(
    col = "activity_category",
    size = 1,
    palette = "Set2",
    title = "Activity category"
  ) +
  tm_layout(
    title = "Visited places by activity category"
  )

visit_frequency <- visits_labelled |>
  st_drop_geometry() |>
  count(placeID, activity_category, sort = TRUE)

visit_points <- visits_labelled |>
  distinct(placeID, .keep_all = TRUE) |>
  left_join(visit_frequency, by = c("placeID", "activity_category"))

tm_shape(visit_points) +
  tm_dots(
    col = "activity_category",
    size = "n",
    palette = "Set2",
    title.col = "Activity category",
    title.size = "Number of visits"
  ) +
  tm_layout(
    title = "Most frequently visited places"
  )

tm_shape(movements) +
  tm_dots(
    col = "transport_mode",
    size = 0.8,
    palette = "Dark2",
    title = "Transport mode"
  ) +
  tm_layout(
    title = "Movement points by transport mode"
  )
```

## Create activity spaces

```{r activity-spaces}
category <- "education"

activity_space_cat <- timeline_sf |>
  filter(record_type == "visit") |>
  filter(activity_category == category) |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_space_cat) +
  tm_polygons(alpha = 0.4) +
  tm_shape(
    timeline_sf |>
      filter(activity_category == category)
  ) +
  tm_dots(size = 0.05)

activity_spaces <- timeline_sf |>
  filter(record_type == "visit") |>
  filter(!is.na(activity_category)) |>
  group_by(activity_category) |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_spaces) +
  tm_polygons(
    col = "activity_category",
    alpha = 0.4
  ) +
  tm_shape(
    timeline_sf |>
      filter(record_type == "visit")
  ) +
  tm_dots(
    col = "activity_category",
    size = 0.05
  )

activity_space_full <- timeline_sf |>
  filter(record_type == "visit") |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_space_full) +
  tm_polygons(alpha = 0.3) +
  tm_shape(
    timeline_sf |>
      filter(record_type == "visit")
  ) +
  tm_dots(size = 0.03)
```

## Load isochrones and POI data

```{r load-isochrones-and-poi}
isochrones_15min <- readRDS("outputs/isochrones_15min.rds") |>
  st_make_valid()

pois_by_iso <- readRDS("outputs/pois_by_iso.rds") |>
  st_make_valid() |>
  recode_poi_categories()

isochrones_15min <- isochrones_15min |>
  st_transform(st_crs(visits_labelled))

pois_by_iso <- pois_by_iso |>
  st_transform(st_crs(visits_labelled))

unique(isochrones_15min$mode)
unique(pois_by_iso$mode)
names(pois_by_iso)
```

## Join actual visits with 15-minute accessibility areas

```{r join-visits-with-isochrones}
visits_labelled_iso <- visits_labelled |>
  mutate(
    within_walk_15 = is_within_mode(geometry, isochrones_15min, "Walking"),
    within_bike_15 = is_within_mode(geometry, isochrones_15min, "Cycling"),
    within_pt_15 = is_within_mode(geometry, isochrones_15min, "Public transport proxy")
  )
```

## Compare actual mobility and theoretical accessibility

```{r compare-mobility-accessibility}
category_crosswalk <- tibble(
  activity_category = analysis_activity_levels,
  poi_activity_category = analysis_activity_levels
)

mobility_table <- visits_labelled_iso |>
  st_drop_geometry() |>
  filter(activity_category != "home") |>
  group_by(activity_category) |>
  summarise(
    n_visits = n(),
    within_walk_15 = sum(within_walk_15, na.rm = TRUE),
    within_bike_15 = sum(within_bike_15, na.rm = TRUE),
    within_pt_15 = sum(within_pt_15, na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(
    share_walk_15 = round(within_walk_15 / n_visits * 100, 1),
    share_bike_15 = round(within_bike_15 / n_visits * 100, 1),
    share_pt_15 = round(within_pt_15 / n_visits * 100, 1)
  ) |>
  arrange(desc(n_visits))

accessibility_table <- pois_by_iso |>
  st_drop_geometry() |>
  group_by(poi_activity_category) |>
  summarise(
    n_pois = n(),
    within_walk_15 = sum(mode == "Walking"),
    within_bike_15 = sum(mode == "Cycling"),
    within_pt_15 = sum(mode == "Public transport proxy"),
    .groups = "drop"
  ) |>
  mutate(
    share_walk_15 = round(within_walk_15 / n_pois * 100, 1),
    share_bike_15 = round(within_bike_15 / n_pois * 100, 1),
    share_pt_15 = round(within_pt_15 / n_pois * 100, 1)
  )

comparison_table <- mobility_table |>
  left_join(category_crosswalk, by = "activity_category") |>
  left_join(
    accessibility_table,
    by = "poi_activity_category",
    suffix = c("_mobility", "_theory")
  )

unmatched_poi_categories <- category_crosswalk |>
  anti_join(accessibility_table, by = "poi_activity_category")

mobility_table
accessibility_table
comparison_table
unmatched_poi_categories
```

## Create summary table

```{r create-summary-table}
summary_table <- comparison_table |>
  transmute(
    Activity = activity_category,
    Visits = n_visits,
    `Walk (%)` = share_walk_15_mobility,
    `Walk Opportunities` = within_walk_15_theory,
    `Bike (%)` = share_bike_15_mobility,
    `Bike Opportunities` = within_bike_15_theory,
    `PT (%)` = share_pt_15_mobility,
    `PT Opportunities` = within_pt_15_theory
  )

summary_table
```

## Visualize activities within 15 minutes

```{r visualize-activities-within-15-minutes}
rq1_data <- summary_table |>
  select(Activity, `Walk (%)`, `Bike (%)`, `PT (%)`) |>
  pivot_longer(
    -Activity,
    names_to = "Mode",
    values_to = "Share"
  )

ggplot(
  rq1_data,
  aes(
    x = reorder(Activity, -Share),
    y = Share,
    fill = Mode
  )
) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(
    x = "",
    y = "% of visits within 15 minutes",
    fill = "Transport mode"
  ) +
  theme_minimal()
```

## Visualize accessibility gap by bike

```{r visualize-accessibility-gap}
access_gap_data <- summary_table |>
  filter(!Activity %in% c("transport", "social")) |>
  mutate(
    `Walk opportunity share (%)` =
      `Walk Opportunities` / sum(`Walk Opportunities`, na.rm = TRUE) * 100,
    `Bike opportunity share (%)` =
      `Bike Opportunities` / sum(`Bike Opportunities`, na.rm = TRUE) * 100,
    `PT opportunity share (%)` =
      `PT Opportunities` / sum(`PT Opportunities`, na.rm = TRUE) * 100
  )

bike_gap <- access_gap_data |>
  transmute(
    Activity,
    `Observed visits within 15 min (%)` = `Bike (%)`,
    `Share of bike-accessible opportunities (%)` = `Bike opportunity share (%)`
  ) |>
  pivot_longer(
    -Activity,
    names_to = "Measure",
    values_to = "Value"
  )

ggplot(
  bike_gap,
  aes(
    x = reorder(Activity, Value),
    y = Value,
    fill = Measure
  )
) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(
    title = "Observed use versus theoretical accessibility by bike",
    subtitle = "Comparison between actual visits within 15 minutes and nearby opportunities",
    x = "",
    y = "%",
    fill = ""
  ) +
  theme_minimal()
```

## Visualize opportunities versus local use

```{r visualize-opportunities-versus-local-use}
vis2_data <- summary_table |>
  filter(!Activity %in% c("transport", "social")) |>
  transmute(
    Activity,
    Opportunities = `Bike Opportunities`,
    LocalUse = `Bike (%)`
  )

scale_factor <- max(vis2_data$Opportunities, na.rm = TRUE) / 100

ggplot(vis2_data, aes(y = reorder(Activity, Opportunities))) +
  geom_segment(
    aes(
      x = 0,
      xend = Opportunities,
      yend = Activity
    ),
    linewidth = 1
  ) +
  geom_point(aes(x = Opportunities), size = 4) +
  geom_point(
    aes(x = LocalUse * scale_factor),
    size = 4,
    shape = 17
  ) +
  scale_x_continuous(
    name = "Accessible opportunities within 15 min by bike",
    sec.axis = sec_axis(
      ~ . / scale_factor,
      name = "Observed activities within 15 min (%)"
    )
  ) +
  labs(
    title = "Accessibility does not necessarily translate into use",
    subtitle = "Nearby opportunities versus observed local activities",
    y = NULL
  ) +
  theme_minimal()
```

## Visualize activities beyond the 15-minute city

```{r visualize-activities-beyond-15-minutes}
outside_visits <- summary_table |>
  mutate(
    outside_bike = round(Visits * (100 - `Bike (%)`) / 100)
  ) |>
  arrange(desc(outside_bike))

ggplot(
  outside_visits,
  aes(
    x = reorder(Activity, outside_bike),
    y = outside_bike
  )
) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Number of visits beyond 15 minutes by bike",
    x = "",
    y = "Number of visits"
  ) +
  theme_minimal()

figure3_bike <- summary_table |>
  filter(!Activity %in% c("transport")) |>
  mutate(
    Beyond_15min = 100 - `Bike (%)`
  ) |>
  arrange(desc(Beyond_15min))

ggplot(
  figure3_bike,
  aes(
    x = reorder(Activity, Beyond_15min),
    y = Beyond_15min
  )
) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Activities occurring beyond 15 minutes by bike",
    x = "",
    y = "% of visits beyond 15 minutes"
  ) +
  theme_minimal()
```

## Prepare isochrone and POI subsets

```{r prepare-isochrone-poi-subsets}
create_output_folders()

isochrones_all <- readRDS("outputs/isochrones_15min.rds") |>
  st_make_valid()

pois_by_iso_all <- readRDS("outputs/pois_by_iso.rds") |>
  st_make_valid()

unique(isochrones_all$mode)
unique(pois_by_iso_all$mode)

modes_all <- c("Walking", "Cycling", "E-bike")
modes_sansebike <- c("Walking", "Cycling")

isochrones_all <- isochrones_all |>
  filter(mode %in% modes_all)

isochrones_sansebike <- isochrones_all |>
  filter(mode %in% modes_sansebike)

pois_by_iso_all <- pois_by_iso_all |>
  filter(mode %in% modes_all)

pois_by_iso_sansebike <- pois_by_iso_all |>
  filter(mode %in% modes_sansebike)

pois_unique_all <- deduplicate_pois(pois_by_iso_all)
pois_unique_sansebike <- deduplicate_pois(pois_by_iso_sansebike)
```

## Recode and save POI subsets

```{r recode-and-save-poi-subsets}
pois_by_iso_all <- recode_poi_categories(pois_by_iso_all)
pois_by_iso_sansebike <- recode_poi_categories(pois_by_iso_sansebike)
pois_unique_all <- recode_poi_categories(pois_unique_all)
pois_unique_sansebike <- recode_poi_categories(pois_unique_sansebike)

saveRDS(isochrones_all, "outputs/isochrones_all/isochrones_all.rds")
saveRDS(isochrones_sansebike, "outputs/isochrones_sansebike/isochrones_sansebike.rds")
saveRDS(pois_by_iso_all, "outputs/pois_all/pois_by_iso_all.rds")
saveRDS(pois_by_iso_sansebike, "outputs/pois_sansebike/pois_by_iso_sansebike.rds")
saveRDS(pois_unique_all, "outputs/pois_all/pois_unique_all.rds")
saveRDS(pois_unique_sansebike, "outputs/pois_sansebike/pois_unique_sansebike.rds")

isochrones_all |>
  st_drop_geometry() |>
  count(mode)

isochrones_sansebike |>
  st_drop_geometry() |>
  count(mode)

pois_by_iso_all |>
  st_drop_geometry() |>
  count(mode, poi_category_original, poi_activity_category, sort = TRUE)

pois_by_iso_sansebike |>
  st_drop_geometry() |>
  count(mode, poi_category_original, poi_activity_category, sort = TRUE)
```

## Prepare data for map visualisations

```{r prepare-map-data}
isochrones_all <- st_transform(isochrones_all, 4326)
isochrones_sansebike <- st_transform(isochrones_sansebike, 4326)

pois_unique_all <- st_transform(pois_unique_all, 4326)
pois_unique_sansebike <- st_transform(pois_unique_sansebike, 4326)

home_sf <- st_transform(home_sf, 4326)

pois_unique_all$poi_activity_category <- as.factor(pois_unique_all$poi_activity_category)
pois_unique_sansebike$poi_activity_category <- as.factor(pois_unique_sansebike$poi_activity_category)

set.seed(123)

poi_levels <- levels(pois_unique_all$poi_activity_category)
poi_colors <- sample(grDevices::rainbow(length(poi_levels), s = 0.8, v = 0.9))
names(poi_colors) <- poi_levels
```

## Map with E-bike

```{r map-with-ebike}
map_pois_all <- 
  mapview(
    isochrones_all[isochrones_all$mode == "E-bike", ],
    col.regions = "lightblue",
    alpha.regions = 0.12,
    color = "deepskyblue4",
    lwd = 5,
    layer.name = "15 min E-bike"
  ) +
  mapview(
    isochrones_all[isochrones_all$mode == "Cycling", ],
    col.regions = "lightgreen",
    alpha.regions = 0.18,
    color = "darkgreen",
    lwd = 5,
    layer.name = "15 min cycling"
  ) +
  mapview(
    isochrones_all[isochrones_all$mode == "Walking", ],
    col.regions = "orange",
    alpha.regions = 0.35,
    color = "darkorange3",
    lwd = 5,
    layer.name = "15 min walking"
  ) +
  mapview(
    pois_unique_all,
    zcol = "poi_activity_category",
    col.regions = poi_colors,
    cex = 3,
    alpha = 0.9,
    layer.name = "POI by activity category"
  ) +
  mapview(
    home_sf,
    col.regions = "red",
    cex = 6,
    layer.name = "Home"
  )

map_pois_all
```

## Map without E-bike

```{r map-without-ebike}
map_pois_sansebike <- 
  mapview(
    isochrones_sansebike[isochrones_sansebike$mode == "Cycling", ],
    col.regions = "lightgreen",
    alpha.regions = 0.18,
    color = "darkgreen",
    lwd = 5,
    layer.name = "15 min cycling"
  ) +
  mapview(
    isochrones_sansebike[isochrones_sansebike$mode == "Walking", ],
    col.regions = "orange",
    alpha.regions = 0.35,
    color = "darkorange3",
    lwd = 5,
    layer.name = "15 min walking"
  ) +
  mapview(
    pois_unique_sansebike,
    zcol = "poi_activity_category",
    col.regions = poi_colors,
    cex = 3,
    alpha = 0.9,
    layer.name = "POI by activity category"
  ) +
  mapview(
    home_sf,
    col.regions = "red",
    cex = 6,
    layer.name = "Home"
  )

map_pois_sansebike
```

## Static map without E-bike

```{r static-map-without-ebike}
iso_sansebike_2056 <- isochrones_sansebike |>
  st_transform(2056)

pois_sansebike_2056 <- pois_unique_sansebike |>
  st_transform(2056)

home_2056 <- home_sf |>
  st_transform(2056)

map_pois_sansebike_black <- ggplot() +
  geom_sf(
    data = iso_sansebike_2056,
    fill = NA,
    color = NA
  ) +
  geom_sf(
    data = iso_sansebike_2056 |> filter(mode == "Cycling"),
    fill = "lightgreen",
    color = "darkgreen",
    alpha = 0.22,
    linewidth = 1
  ) +
  geom_sf(
    data = iso_sansebike_2056 |> filter(mode == "Walking"),
    fill = "orange",
    color = "darkorange",
    alpha = 0.35,
    linewidth = 1
  ) +
  geom_sf(
    data = pois_sansebike_2056,
    aes(color = poi_activity_category),
    size = 1.6,
    alpha = 0.9
  ) +
  geom_sf(
    data = home_2056,
    color = "red",
    size = 3
  ) +
  labs(
    title = "15-minute accessibility without E-bike",
    subtitle = "Walking and cycling isochrones with relevant POI",
    color = "POI category"
  ) +
  theme_void() +
  theme(
    plot.background = element_rect(fill = "black", color = NA),
    panel.background = element_rect(fill = "black", color = NA),
    legend.background = element_rect(fill = "black", color = NA),
    legend.key = element_rect(fill = "black", color = NA),
    legend.text = element_text(color = "white"),
    legend.title = element_text(color = "white"),
    plot.title = element_text(color = "white", face = "bold"),
    plot.subtitle = element_text(color = "white")
  )

map_pois_sansebike_black
```
