---
title: "Data_preprocessing"
format: html
---

```{r}
library(jsonlite)
library(tidyverse)
library(lubridate)
library(sf)
library(ggplot2)
library(tmap)
library(leaflet)
library(mapview)
```

## Importing the google timeline

```{r}

timeline_raw <- fromJSON("timeline.json", flatten = TRUE)

names(timeline_raw)
glimpse(timeline_raw)



```

## Cleaning of the dataset, keep only relevant

```{r}
#convert timestamps into movement data. 

timeline <- timeline_raw |>
  mutate(
    start_time = ymd_hms(startTime),
    end_time = ymd_hms(endTime),
    duration_min = as.numeric(difftime(end_time, start_time, units = "mins")),
    date = as_date(start_time),
    weekday = wday(start_time, label = TRUE, week_start = 1),
    hour = hour(startTime),

    record_type = case_when(
      !is.na(activity.distanceMeters) ~ "movement",
      !is.na(visit.probability) ~ "visit",
      TRUE ~ "unknown"
    ),

    location = case_when(
      record_type == "movement" ~ activity.start,
      record_type == "visit" ~ visit.topCandidate.placeLocation
    ),

    lat = as.numeric(str_extract(location, "(?<=geo:)[0-9.\\-]+")),
    lon = as.numeric(str_extract(location, "(?<=,)[0-9.\\-]+")),

    transport_mode = activity.topCandidate.type,
    placeID = visit.topCandidate.placeID,
    activity_category = NA_character_
  ) |>
  select(start_time, end_time, duration_min, date, weekday,
         record_type, transport_mode, activity_category,
         placeID, lat, lon) |>
  filter(!is.na(lat), !is.na(lon)) |>
  arrange(start_time)


```

## convert to spatial object 

```{r}
#Convert table into Spatial object

timeline_sf <- timeline |>
  st_as_sf(coords = c("lon", "lat"), crs = 4326) |>
  st_transform(2056)

# separate coordinates in 2 columns like the Sabi example.
coords <- st_coordinates(timeline_sf)

timeline_sf <- timeline_sf |>
  mutate(
    E = coords[, 1],
    N = coords[, 2]
  )
```

## Semantic Annotation of Activity categories

### Semantic annotation categories
```{r}
activity_categories <- tibble::tribble(
  ~category, ~includes,

  "transport", "Train stations, tram stops, bus stops, airports - probably to be filtered out",
  "home", "Residence",
  "education", "University, school",
  "work", "Workplace",
  "shopping", "Supermarket, stores, post office",
  "leisure", "Restaurants, bars, cinema, culture",
  "sport", "Gym, climbing, swimming",
  "nature", "Hikes, parks, mountains",
  "social", "Friends/family",
  "movement", "No POI (reclassify to movement as record type instead of visit)",
  "healthcare", "Doctor, pharmacy",
  "unknown", "Unresolved"
)

activity_categories
```


```{r}
#creates one row per unique visited place
visits <- timeline_sf |>
  filter(record_type == "visit") |>
  distinct(placeID, .keep_all = TRUE) |>
  arrange(placeID) |>
  mutate(
    place_number = row_number()
  )
timeline_sf <- timeline_sf |>
  left_join(
    visits |>
      st_drop_geometry() |>
      select(placeID, place_number),
    by = "placeID"
  )

mapview::mapview(visits)

# manual labelling 
visits <- visits |>
  mutate(
    activity_category = case_when(
      place_number == 1 ~ "shopping",
      place_number == 2 ~ "movement",
      place_number == 3 ~ "leisure",
      place_number == 4 ~ "movement",
      place_number == 5 ~ "work",
      place_number == 6 ~ "transport",
      place_number == 7 ~ "social",
      place_number == 8 ~ "transport",
      place_number == 9 ~ "education",
      place_number == 10 ~ "movement",
      place_number == 11 ~ "social",
      place_number == 12 ~ "nature",
      place_number == 13 ~ "sport",
      place_number == 14 ~ "education",
      place_number == 15 ~ "healthcare",
      place_number == 16 ~ "shopping",
      place_number == 17 ~ "movement",
      place_number == 18 ~ "education",
      place_number == 19 ~ "leisure",
      place_number == 20 ~ "transport",
      place_number == 21 ~ "leisure",
      place_number == 22 ~ "movement",
      place_number == 23 ~ "movement",
      place_number == 24 ~ "shopping",
      place_number == 25 ~ "transport",
      place_number == 26 ~ "shopping",
      place_number == 27 ~ "movement",
      place_number == 28 ~ "movement",
      place_number == 29 ~ "social",
      place_number == 30 ~ "social",
      place_number == 31 ~ "leisure",
      place_number == 32 ~ "movement",
      place_number == 33 ~ "transport",
      place_number == 34 ~ "sport",
      place_number == 35 ~ "movement",
      place_number == 36 ~ "transport",
      place_number == 37 ~ "sport",
      place_number == 38 ~ "social",
      place_number == 39 ~ "leisure",
      place_number == 40 ~ "shopping",
      place_number == 41 ~ "leisure",
      place_number == 42 ~ "shopping",
      place_number == 43 ~ "leisure",
      place_number == 44 ~ "movement",
      place_number == 45 ~ "leisure",
      place_number == 46 ~ "leisure",
      place_number == 47 ~ "nature",
      place_number == 48 ~ "movement",
      place_number == 49 ~ "social",
      place_number == 50 ~ "transport",
      place_number == 51 ~ "movement",
      place_number == 52 ~ "nature",
      place_number == 53 ~ "movement",
      place_number == 54 ~ "movement",
      place_number == 55 ~ "movement",
      place_number == 56 ~ "shopping",
      place_number == 57 ~ "education",
      place_number == 58 ~ "nature",
      place_number == 59 ~ "nature",
      place_number == 60 ~ "transport",
      place_number == 61 ~ "social",
      place_number == 62 ~ "nature",
      place_number == 63 ~ "social",
      place_number == 64 ~ "shopping",
      place_number == 65 ~ "healthcare",
      place_number == 66 ~ "social",
      place_number == 67 ~ "movement",
      place_number == 68 ~ "sport",
      place_number == 69 ~ "movement",
      place_number == 70 ~ "movement",
      place_number == 71 ~ "transport",
      place_number == 72 ~ "shopping",
      place_number == 73 ~ "movement",
      place_number == 74 ~ "movement",
      place_number == 75 ~ "movement",
      place_number == 76 ~ "nature",
      place_number == 77 ~ "social",
      place_number == 78 ~ "leisure",
      place_number == 79 ~ "nature",
      place_number == 80 ~ "social",
      place_number == 81 ~ "social",
      place_number == 82 ~ "movement",
      place_number == 83 ~ "shopping",
      place_number == 84 ~ "transport",
      place_number == 85 ~ "movement",
      place_number == 86 ~ "movement",
      place_number == 87 ~ "leisure",
      place_number == 88 ~ "transport",
      place_number == 89 ~ "healthcare",
      place_number == 90 ~ "transport",
      place_number == 91 ~ "education",
      place_number == 92 ~ "nature",
      place_number == 93 ~ "shopping",
      place_number == 94 ~ "movement",
      place_number == 95 ~ "transport",
      place_number == 96 ~ "movement",
      place_number == 97 ~ "shopping",
      place_number == 98 ~ "education",
      place_number == 99 ~ "education",
      place_number == 100 ~ "transport",
      place_number == 101 ~ "movement",
      place_number == 102 ~ "movement",
      place_number == 103 ~ "social",
      place_number == 104 ~ "leisure",
      place_number == 105 ~ "shopping",
      place_number == 106 ~ "shopping",
      place_number == 107 ~ "shopping",
      place_number == 108 ~ "movement",
      place_number == 109 ~ "shopping",
      place_number == 110 ~ "transport",
      place_number == 111 ~ "leisure",
      place_number == 112 ~ "movement",
      place_number == 113 ~ "movement",
      place_number == 114 ~ "movement",
      place_number == 115 ~ "social",
      place_number == 116 ~ "movement",
      place_number == 117 ~ "shopping",
      place_number == 118 ~ "shopping",
      place_number == 119 ~ "movement",
      place_number == 120 ~ "transport",
      place_number == 121 ~ "shopping",
      place_number == 122 ~ "transport",
      place_number == 123 ~ "leisure",
      place_number == 124 ~ "shopping",
      place_number == 125 ~ "education",
      place_number == 126 ~ "nature",
      place_number == 127 ~ "leisure",
      place_number == 128 ~ "shopping",
      place_number == 129 ~ "social",
      place_number == 130 ~ "transport",
      place_number == 131 ~ "transport",
      place_number == 132 ~ "healthcare",
      place_number == 133 ~ "movement",
      place_number == 134 ~ "movement",
      place_number == 135 ~ "transport",
      place_number == 136 ~ "leisure",
      place_number == 137 ~ "leisure",
      place_number == 138 ~ "movement",
      place_number == 139 ~ "movement",
      place_number == 140 ~ "leisure",
      place_number == 141 ~ "shopping",
      place_number == 142 ~ "transport",
      place_number == 143 ~ "education",
      place_number == 144 ~ "home",
      place_number == 145 ~ "transport",
      place_number == 146 ~ "social",
      place_number == 147 ~ "social",
      place_number == 148 ~ "nature",
      place_number == 149 ~ "movement",
      place_number == 150 ~ "movement",
      place_number == 151 ~ "education",
      place_number == 152 ~ "movement",
      place_number == 153 ~ "leisure",
      place_number == 154 ~ "transport",
      place_number == 155 ~ "shopping",
      place_number == 156 ~ "transport",
      place_number == 157 ~ "movement",
      place_number == 158 ~ "movement",
      place_number == 159 ~ "education",
      place_number == 160 ~ "movement",
      place_number == 161 ~ "sport",
      place_number == 162 ~ "education",
      place_number == 163 ~ "sport",
      place_number == 164 ~ "sport",
      place_number == 165 ~ "leisure",
      place_number == 166 ~ "nature",
      place_number == 167 ~ "social",
      TRUE ~ "unknown"
    )
  )


```

## Merging the labelling to the dataset

```{r}
timeline_sf <- timeline_sf |>
  left_join(
    visits |>
      st_drop_geometry() |>
      select(placeID, activity_category),
    by = "placeID",
    suffix = c("", "_labelled")
  ) |>
  mutate(
    activity_category = coalesce(activity_category_labelled, activity_category)
  ) |>
  select(-activity_category_labelled)

timeline_sf |>
  filter(record_type == "visit") |>
  count(activity_category, sort = TRUE)

# si category_type movement, reclassify in record type 
timeline_sf <- timeline_sf |>
  mutate(
    record_type = case_when(
      activity_category == "movement" ~ "movement",
      TRUE ~ record_type
    ),
    activity_category = case_when(
      activity_category == "movement" ~ NA_character_,
      TRUE ~ activity_category
    )
  )

movements <- timeline_sf |> filter(record_type == "movement")
visits_labelled <- timeline_sf |> filter(record_type == "visit")



```


## Visualize

```{r}
# Visits by activity category
tm_shape(visits_labelled) +
  tm_dots(
    col = "activity_category",
    size = 1,
    palette = "Set2",
    title = "Activity category"
  ) +
  tm_layout(
    title = "Visited places by activity category"
  )
tmap_mode("view")


# Unique visited places, sized by frequency
visit_frequency <- visits_labelled |>
  st_drop_geometry() |>
  count(placeID, activity_category, sort = TRUE)

visit_points <- visits_labelled |>
  distinct(placeID, .keep_all = TRUE) |>
  left_join(visit_frequency, by = c("placeID", "activity_category"))

tm_shape(visit_points) +
  tm_dots(
    col = "activity_category",
    size = "n",
    palette = "Set2",
    title.col = "Activity category",
    title.size = "Number of visits"
  ) +
  tm_layout(
    title = "Most frequently visited places"
  )

# Movements by transport mode

tm_shape(movements) +
  tm_dots(
    col = "transport_mode",
    size = 0.8,
    palette = "Dark2",
    title = "Transport mode"
  ) +
  tm_layout(
    title = "Movement points by transport mode"
  )

```
## Activity shape per activity category

```{r}

# for one category
category <- "education"

activity_space_cat <- timeline_sf |>
  filter(record_type == "visit") |>
  filter(activity_category == category) |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_space_cat) +
  tm_polygons(alpha = 0.4) +
tm_shape(
  timeline_sf |>
    filter(activity_category == category)
) +
  tm_dots(size = 0.05)

# for all categories
activity_spaces <- timeline_sf |>
  filter(record_type == "visit") |>
  filter(!is.na(activity_category)) |>
  group_by(activity_category) |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_spaces) +
  tm_polygons(
    col = "activity_category",
    alpha = 0.4
  ) +
tm_shape(
  timeline_sf |>
    filter(record_type == "visit")
) +
  tm_dots(
    col = "activity_category",
    size = 0.05
  )

# full activity space
activity_space_full <- timeline_sf |>
  filter(record_type == "visit") |>
  summarise() |>
  st_convex_hull()

tm_shape(activity_space_full) +
  tm_polygons(
    alpha = 0.3
  ) +
tm_shape(
  timeline_sf |>
    filter(record_type == "visit")
) +
  tm_dots(size = 0.03)

```
## integration of isochrones

```{r}
#load the saved objects 
isochrones_15min <- readRDS("outputs/isochrones_15min.rds")
pois_by_iso <- readRDS("outputs/pois_by_iso.rds")

#Make sure CRS match
isochrones_15min <- st_transform(
  isochrones_15min,
  st_crs(visits_labelled)
)

# join isochrones to visited places
visits_labelled_iso <- visits_labelled |>
  mutate(
    within_walk_15 =
      lengths(st_within(
        geometry,
        isochrones_15min[isochrones_15min$mode == "Walking", ]
      )) > 0,

    within_bike_15 =
      lengths(st_within(
        geometry,
        isochrones_15min[isochrones_15min$mode == "Cycling", ]
      )) > 0,

    within_pt_15 =
      lengths(st_within(
        geometry,
        isochrones_15min[isochrones_15min$mode == "Public transport proxy", ]
      )) > 0
  )


```
## match activity category of point of interest with activity categories of mobility data. 

```{r}
category_crosswalk <- tibble(
  activity_category = c(
    "shopping",
    "nature",
    "healthcare",
    "leisure",
    "sport",
    "education",
    "work"
  ),
  poi_category = c(
    "Groceries",
    "Park / forest",
    "Pharmacy / doctor",
    "Restaurants",
    "Sport",
    "University",
    "Work"
  )
)

```



## Results

```{r}
# practice
mobility_table <- visits_labelled_iso |>
  st_drop_geometry() |>
  filter(activity_category != "home") |>
  group_by(activity_category) |>
  summarise(
    n_visits = n(),
    within_walk_15 = sum(within_walk_15, na.rm = TRUE),
    within_bike_15 = sum(within_bike_15, na.rm = TRUE),
    within_pt_15 = sum(within_pt_15, na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(
    share_walk_15 = round(within_walk_15 / n_visits * 100, 1),
    share_bike_15 = round(within_bike_15 / n_visits * 100, 1),
    share_pt_15 = round(within_pt_15 / n_visits * 100, 1)
  ) |>
  arrange(desc(n_visits))

#in theory
accessibility_table <- pois_by_iso |>
  st_drop_geometry() |>
  group_by(poi_category) |>
  summarise(
    n_pois = n(),

    within_walk_15 = sum(mode == "Walking"),
    within_bike_15 = sum(mode == "Cycling"),
    within_pt_15 = sum(mode == "Public transport proxy"),

    .groups = "drop"
  ) |>
  mutate(
    share_walk_15 = round(within_walk_15 / n_pois * 100, 1),
    share_bike_15 = round(within_bike_15 / n_pois * 100, 1),
    share_pt_15 = round(within_pt_15 / n_pois * 100, 1)
  )

names(pois_by_iso)

# match the categories
comparison_table <- mobility_table |>
  left_join(
    category_crosswalk,
    by = "activity_category"
  ) |>
  left_join(
    accessibility_table,
    by = "poi_category",
    suffix = c("_mobility", "_theory")
  )
category_crosswalk |>
  anti_join(
    accessibility_table,
    by = "poi_category"
  )
```

## Join the actual mobility and theoretical accessibility
```{r}
summary_table <- mobility_table |>
  left_join(
    category_crosswalk,
    by = "activity_category"
  ) |>
  left_join(
    accessibility_table,
    by = "poi_category",
    suffix = c("_mobility", "_theory")
  ) |>
  transmute(
    Activity = activity_category,
    Visits = n_visits,

    `Walk (%)` = share_walk_15_mobility,
    `Walk Opportunities` = within_walk_15_theory,

    `Bike (%)` = share_bike_15_mobility,
    `Bike Opportunities` = within_bike_15_theory,

    `PT (%)` = share_pt_15_mobility,
    `PT Opportunities` = within_pt_15_theory
  )
```

## Visualisation 

### What proportion of activities occur within 15 minutes?

```{r}


rq1_data <- summary_table |>
  select(Activity, `Walk (%)`, `Bike (%)`, `PT (%)`) |>
  pivot_longer(
    -Activity,
    names_to = "Mode",
    values_to = "Share"
  )
# as a frouped bar chart
ggplot(rq1_data,
       aes(x = reorder(Activity, -Share),
           y = Share,
           fill = Mode)) +
  geom_col(position = "dodge") +
  labs(
    x = "",
    y = "% of visits within 15 minutes",
    fill = "Transport mode"
  ) +
  theme_minimal() +
  coord_flip()

```

### Accessibility Gap
only the cycling isochrone was used here

```{r}

access_gap_data <- summary_table |>
  filter(!Activity %in% c("transport", "social")) |>
  mutate(
    `Walk opportunity share (%)` =
      `Walk Opportunities` / sum(`Walk Opportunities`, na.rm = TRUE) * 100,
    `Bike opportunity share (%)` =
      `Bike Opportunities` / sum(`Bike Opportunities`, na.rm = TRUE) * 100,
    `PT opportunity share (%)` =
      `PT Opportunities` / sum(`PT Opportunities`, na.rm = TRUE) * 100
  )

bike_gap <- access_gap_data |>
  transmute(
    Activity,
    `Observed visits within 15 min (%)` = `Bike (%)`,
    `Share of bike-accessible opportunities (%)` = `Bike opportunity share (%)`
  ) |>
  pivot_longer(
    -Activity,
    names_to = "Measure",
    values_to = "Value"
  )

ggplot(
  bike_gap,
  aes(
    x = reorder(Activity, Value),
    y = Value,
    fill = Measure
  )
) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(
    title = "Observed use versus theoretical accessibility by bike",
    subtitle = "Comparison between actual visits within 15 minutes and nearby opportunities",
    x = "",
    y = "%",
    fill = ""
  ) +
  theme_minimal()


```


```{r}
vis2_data <- summary_table |>
  filter(!Activity %in% c("transport", "social")) |>
  transmute(
    Activity,
    Opportunities = `Bike Opportunities`,
    LocalUse = `Bike (%)`
  )

# scaling factor for secondary axis
scale_factor <- max(vis2_data$Opportunities) / 100

ggplot(vis2_data,
       aes(y = reorder(Activity, Opportunities))) +

  # line
  geom_segment(
    aes(
      x = 0,
      xend = Opportunities,
      yend = Activity
    ),
    linewidth = 1
  ) +

  # opportunity point
  geom_point(
    aes(x = Opportunities),
    size = 4
  ) +

  # local-use point
  geom_point(
    aes(x = LocalUse * scale_factor),
    size = 4,
    shape = 17
  ) +

  scale_x_continuous(
    name = "Accessible opportunities within 15 min by bike",
    sec.axis = sec_axis(
      ~ . / scale_factor,
      name = "Observed activities within 15 min (%)"
    )
  ) +

  labs(
    title = "Accessibility does not necessarily translate into use",
    subtitle = "Nearby opportunities versus observed local activities",
    y = NULL
  ) +

  theme_minimal()
```


### Activities occurring beyond the 15-minute city 

only the cycling isochrone was used here
```{r}
#considering the absolute frequency of visits 
outside_visits <- summary_table |>
  mutate(
    outside_bike = round(Visits * (100 - `Bike (%)`) / 100)
  ) |>
  arrange(desc(outside_bike))

ggplot(outside_visits,
       aes(reorder(Activity, outside_bike),
           outside_bike)) +
  geom_col() +
  coord_flip()

# considering relative frequency.( invert from research question 1)
figure3_bike <- summary_table |>
  filter(!Activity %in% c("transport")) |>
  mutate(
    Beyond_15min = 100 - `Bike (%)`
  ) |>
  arrange(desc(Beyond_15min))

ggplot(
  figure3_bike,
  aes(
    x = reorder(Activity, Beyond_15min),
    y = Beyond_15min
  )
) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Activities occurring beyond 15 minutes by bike",
    x = "",
    y = "% of visits beyond 15 minutes"
  ) +
  theme_minimal()

```

## Experimental activity classification model
```{r}
library(caret)
library(randomForest)

# 1. Prepare labelled visit data
activity_model_data <- visits_labelled_iso |>
  st_drop_geometry() |>
  filter(
    !is.na(activity_category),
    !activity_category %in% c("home", "movement", "unknown")
  ) |>
  mutate(
    hour = hour(start_time),
    weekday = as.factor(weekday),
    is_weekend = weekday %in% c("Sat", "Sun"),
    time_period = case_when(
      hour >= 6  & hour < 10 ~ "morning",
      hour >= 10 & hour < 17 ~ "day",
      hour >= 17 & hour < 22 ~ "evening",
      TRUE ~ "night"
    ),
    duration_min = as.numeric(duration_min),
    activity_category = as.factor(activity_category)
  ) |>
  select(
    activity_category,
    duration_min,
    hour,
    weekday,
    is_weekend,
    time_period,
    within_walk_15,
    within_bike_15,
    within_pt_15
  ) |>
  drop_na()


# 2. Train-test split
set.seed(123)

train_index <- createDataPartition(
  activity_model_data$activity_category,
  p = 0.8,
  list = FALSE
)

train_data <- activity_model_data[train_index, ]
test_data  <- activity_model_data[-train_index, ]


# 3. Train Random Forest model
rf_activity_model <- randomForest(
  activity_category ~ .,
  data = train_data,
  ntree = 500,
  importance = TRUE
)


# 4. Predict activity categories
activity_predictions <- predict(
  rf_activity_model,
  newdata = test_data
)


# 5. Evaluate model
confusionMatrix(
  activity_predictions,
  test_data$activity_category
)


# 6. Variable importance
varImpPlot(rf_activity_model)


```
##Noémie part
#New try with isochrones for all modes or only some of the modes
```{r}

library(sf)
library(dplyr)

# ------------------------------------------------------------
# Create clear versions of isochrones and POI
# - isochrones_all = Walking + Cycling + E-bike
# - isochrones_sansebike = Walking + Cycling
# - same logic for POI
# ------------------------------------------------------------

# 1. Load saved files
isochrones_all <- readRDS("outputs/isochrones_15min.rds") |>
  st_make_valid()

pois_by_iso_all <- readRDS("outputs/pois_by_iso.rds") |>
  st_make_valid()

# 2. Check available modes
unique(isochrones_all$mode)
unique(pois_by_iso_all$mode)

# 3. Define mode groups
modes_all <- c("Walking", "Cycling", "E-bike")
modes_sansebike <- c("Walking", "Cycling")

# 4. Create isochrone subsets
isochrones_all <- isochrones_all |>
  filter(mode %in% modes_all)

isochrones_sansebike <- isochrones_all |>
  filter(mode %in% modes_sansebike)

# 5. Create POI subsets
# This keeps the POI-mode relation, useful for counts by mode
pois_by_iso_all <- pois_by_iso_all |>
  filter(mode %in% modes_all)

pois_by_iso_sansebike <- pois_by_iso_all |>
  filter(mode %in% modes_sansebike)

# 6. Create unique POI versions for visualisation
# This avoids plotting the same POI several times if it is inside several isochrones
deduplicate_pois <- function(x) {
  
  dedup_cols <- intersect(
    c("osm_id", "name", "poi_category", "poi_subcategory"),
    names(x)
  )
  
  if (length(dedup_cols) > 0) {
    x <- x |>
      distinct(across(all_of(dedup_cols)), .keep_all = TRUE)
  }
  
  return(x)
}

pois_unique_all <- deduplicate_pois(pois_by_iso_all)
pois_unique_sansebike <- deduplicate_pois(pois_by_iso_sansebike)

# 7. Create clear folders
dir.create("outputs/isochrones_all", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/isochrones_sansebike", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/pois_all", recursive = TRUE, showWarnings = FALSE)
dir.create("outputs/pois_sansebike", recursive = TRUE, showWarnings = FALSE)

# 8. Save RDS files
saveRDS(
  isochrones_all,
  "outputs/isochrones_all/isochrones_all.rds"
)

saveRDS(
  isochrones_sansebike,
  "outputs/isochrones_sansebike/isochrones_sansebike.rds"
)

saveRDS(
  pois_by_iso_all,
  "outputs/pois_all/pois_by_iso_all.rds"
)

saveRDS(
  pois_by_iso_sansebike,
  "outputs/pois_sansebike/pois_by_iso_sansebike.rds"
)

saveRDS(
  pois_unique_all,
  "outputs/pois_all/pois_unique_all.rds"
)

saveRDS(
  pois_unique_sansebike,
  "outputs/pois_sansebike/pois_unique_sansebike.rds"
)


# 10. Quick checks
isochrones_all |>
  st_drop_geometry() |>
  count(mode)

isochrones_sansebike |>
  st_drop_geometry() |>
  count(mode)

pois_by_iso_all |>
  st_drop_geometry() |>
  count(mode, poi_category, sort = TRUE)

pois_by_iso_sansebike |>
  st_drop_geometry() |>
  count(mode, poi_category, sort = TRUE)

```
#Adapt the names to the new POI 
```{r}
# ------------------------------------------------------------
# Adapt POI category names to match Lucie's activity categories
# This is applied to all POI objects, including E-bike POI
# ------------------------------------------------------------

library(dplyr)
library(sf)

# Function to recode POI categories into project activity categories
recode_poi_categories <- function(x) {
  
  x |>
    mutate(
      poi_category_original = poi_category,
      
      poi_activity_category = case_when(
        poi_category == "Groceries" ~ "shopping",
        poi_category == "Park / forest" ~ "nature",
        poi_category == "Pharmacy / doctor" ~ "healthcare",
        poi_category == "Restaurants" ~ "leisure",
        poi_category == "Sport" ~ "sport",
        poi_category == "University" ~ "education",
        poi_category == "Work" ~ "work",
        TRUE ~ "unknown"
      ),
      
      poi_activity_category = factor(
        poi_activity_category,
        levels = c(
          "shopping",
          "nature",
          "healthcare",
          "leisure",
          "sport",
          "education",
          "work",
          "unknown"
        )
      )
    )
}

# Apply to all POI datasets
pois_by_iso_all <- recode_poi_categories(pois_by_iso_all)
pois_by_iso_sansebike <- recode_poi_categories(pois_by_iso_sansebike)

pois_unique_all <- recode_poi_categories(pois_unique_all)
pois_unique_sansebike <- recode_poi_categories(pois_unique_sansebike)

# New crosswalk becomes simple and coherent
category_crosswalk <- tibble(
  activity_category = c(
    "shopping",
    "nature",
    "healthcare",
    "leisure",
    "sport",
    "education",
    "work"
  ),
  poi_activity_category = c(
    "shopping",
    "nature",
    "healthcare",
    "leisure",
    "sport",
    "education",
    "work"
  )
)

# Quick check
pois_by_iso_all |>
  st_drop_geometry() |>
  count(mode, poi_category_original, poi_activity_category, sort = TRUE)

pois_by_iso_sansebike |>
  st_drop_geometry() |>
  count(mode, poi_category_original, poi_activity_category, sort = TRUE)

# Save updated versions
saveRDS(
  pois_by_iso_all,
  "outputs/pois_all/pois_by_iso_all.rds"
)

saveRDS(
  pois_by_iso_sansebike,
  "outputs/pois_sansebike/pois_by_iso_sansebike.rds"
)

saveRDS(
  pois_unique_all,
  "outputs/pois_all/pois_unique_all.rds"
)

saveRDS(
  pois_unique_sansebike,
  "outputs/pois_sansebike/pois_unique_sansebike.rds"
)
```
#Visualisation de la map
```{r}
# Visualisations
# 1. Map with E-bike
# 2. Map without E-bike
# 3. Map without E-bike and without basemap, black background
# ------------------------------------------------------------

library(sf)
library(dplyr)
library(mapview)
library(ggplot2)

# Home point, if not already loaded
home_sf <- st_sf(
  geometry = st_sfc(st_point(c(8.546069, 47.409620))),
  crs = 4326
)

# Make sure everything has the same CRS for mapview
isochrones_all <- st_transform(isochrones_all, 4326)
isochrones_sansebike <- st_transform(isochrones_sansebike, 4326)

pois_unique_all <- st_transform(pois_unique_all, 4326)
pois_unique_sansebike <- st_transform(pois_unique_sansebike, 4326)

home_sf <- st_transform(home_sf, 4326)

# Make POI categories categorical
pois_unique_all$poi_activity_category <- as.factor(pois_unique_all$poi_activity_category)
pois_unique_sansebike$poi_activity_category <- as.factor(pois_unique_sansebike$poi_activity_category)

# Create stable random-looking colors for POI categories
set.seed(123)

poi_levels <- levels(pois_unique_all$poi_activity_category)

poi_colors <- sample(
  grDevices::rainbow(length(poi_levels), s = 0.8, v = 0.9)
)

names(poi_colors) <- poi_levels

# ------------------------------------------------------------
# 1. Map with E-bike
# ------------------------------------------------------------

map_pois_all <- 
  mapview(
    isochrones_all[isochrones_all$mode == "E-bike", ],
    col.regions = "lightblue",
    alpha.regions = 0.12,
    color = "deepskyblue4",
    lwd = 5,
    layer.name = "15 min E-bike"
  ) +
  mapview(
    isochrones_all[isochrones_all$mode == "Cycling", ],
    col.regions = "lightgreen",
    alpha.regions = 0.18,
    color = "darkgreen",
    lwd = 5,
    layer.name = "15 min cycling"
  ) +
  mapview(
    isochrones_all[isochrones_all$mode == "Walking", ],
    col.regions = "orange",
    alpha.regions = 0.35,
    color = "darkorange3",
    lwd = 5,
    layer.name = "15 min walking"
  ) +
  mapview(
    pois_unique_all,
    zcol = "poi_activity_category",
    col.regions = poi_colors,
    cex = 3,
    alpha = 0.9,
    layer.name = "POI by activity category"
  ) +
  mapview(
    home_sf,
    col.regions = "red",
    cex = 6,
    layer.name = "Home"
  )

map_pois_all


# ------------------------------------------------------------
# 2. Map without E-bike
# ------------------------------------------------------------

map_pois_sansebike <- 
  mapview(
    isochrones_sansebike[isochrones_sansebike$mode == "Cycling", ],
    col.regions = "lightgreen",
    alpha.regions = 0.18,
    color = "darkgreen",
    lwd = 5,
    layer.name = "15 min cycling"
  ) +
  mapview(
    isochrones_sansebike[isochrones_sansebike$mode == "Walking", ],
    col.regions = "orange",
    alpha.regions = 0.35,
    color = "darkorange3",
    lwd = 5,
    layer.name = "15 min walking"
  ) +
  mapview(
    pois_unique_sansebike,
    zcol = "poi_activity_category",
    col.regions = poi_colors,
    cex = 3,
    alpha = 0.9,
    layer.name = "POI by activity category"
  ) +
  mapview(
    home_sf,
    col.regions = "red",
    cex = 6,
    layer.name = "Home"
  )

map_pois_sansebike


# ------------------------------------------------------------
# 3. Static map without E-bike and without basemap
# Black background, no coordinates shown
# ------------------------------------------------------------

# Transform to metric CRS for a clean static plot
iso_sansebike_2056 <- isochrones_sansebike |>
  st_transform(2056)

pois_sansebike_2056 <- pois_unique_sansebike |>
  st_transform(2056)

home_2056 <- home_sf |>
  st_transform(2056)

map_pois_sansebike_black <- ggplot() +
  
  # Black background area
  geom_sf(
    data = iso_sansebike_2056,
    fill = NA,
    color = NA
  ) +
  
  # Cycling isochrone
  geom_sf(
    data = iso_sansebike_2056 |> filter(mode == "Cycling"),
    fill = "lightgreen",
    color = "darkgreen",
    alpha = 0.22,
    linewidth = 1
  ) +
  
  # Walking isochrone
  geom_sf(
    data = iso_sansebike_2056 |> filter(mode == "Walking"),
    fill = "orange",
    color = "darkorange",
    alpha = 0.35,
    linewidth = 1
  ) +
  
  # POI
  geom_sf(
    data = pois_sansebike_2056,
    aes(color = poi_activity_category),
    size = 1.6,
    alpha = 0.9
  ) +
  
  # Home
  geom_sf(
    data = home_2056,
    color = "red",
    size = 3
  ) +
  
  labs(
    title = "15-minute accessibility without E-bike",
    subtitle = "Walking and cycling isochrones with relevant POI",
    color = "POI category"
  ) +
  
  theme_void() +
  theme(
    plot.background = element_rect(fill = "black", color = NA),
    panel.background = element_rect(fill = "black", color = NA),
    legend.background = element_rect(fill = "black", color = NA),
    legend.key = element_rect(fill = "black", color = NA),
    legend.text = element_text(color = "white"),
    legend.title = element_text(color = "white"),
    plot.title = element_text(color = "white", face = "bold"),
    plot.subtitle = element_text(color = "white")
  )

map_pois_sansebike_black
```



