---
title: The 15-Minute City in Practice
subtitle: Comparing Theoretical Accessibility and Actual Mobility Behavior in Zurich
author: Lucie Kern and Noémie Simon
format:
  html:
    code-fold: true
execute:
  warning: false
  message: false
lang: en  
bibliography: bibliography.bib
---

```{r preprocessing}
#| code-summary: preprocessing

``` 


## Abstract

## Introduction

@laube2011 investigate how temporal scale affects the calculation of movement parameters (speed, sinuosity and turning angle) of animal trajectories. 

--> literatur review on 15 minutes cities!

## Material and Methods

All spatial analyses were conducted in R (R Core Team, 2025) using the RStudio integrated development environment (Posit team, 2025). The workflow relied on several R packages for data import, manipulation, spatial analysis and visualisation. Google Timeline data were imported using `jsonlite`, while data processing and transformation were performed using the `tidyverse` ecosystem, including `dplyr`, `tidyr`, `purrr` and `tibble`. Temporal information was handled using `lubridate`. Spatial analyses were conducted using `sf`, which was used for coordinate transformations, spatial operations and geometry processing. OpenStreetMap data were retrieved using `osmdata`, and network-based accessibility analyses were performed with `dodgr`. Visualisations were created using `ggplot2`, `tmap` and `mapview` for statistical graphics and interactive maps.

### Study area and origin point

The analysis focused on the residential environment of the analysed individual in Zurich. The home location was defined as the origin point for the accessibility analysis. To ensure accurate spatial operations, the origin was first stored as a simple feature object in WGS84 coordinates and then transformed into the Swiss projected coordinate reference system LV95, EPSG:2056. A buffer of 6 km was created around the origin point and subsequently transformed back to WGS84. This buffered bounding box was used to download the relevant OpenStreetMap street network for the local study area.

### Street network and transport modes

The street network was obtained from OpenStreetMap using the `dodgr_streetnet()` function. Based on this network, three weighted graphs were created to represent different transport modes: walking, cycling, and a simplified public transport proxy. The walking graph was weighted using the foot profile, the cycling graph using the bicycle profile, and the public transport proxy using the motorcar profile. The latter does not represent exact public transport routes, stops, schedules, waiting times, or transfers. Instead, it was used as a simplified approximation of faster network-based accessibility within the urban transport system.

For each transport mode, the home location was snapped to the nearest connected vertex of the corresponding network graph. Network distances from this origin vertex to all other vertices were then calculated using `dodgr_dists()`. Reachable vertices were selected based on the maximum distance that could be travelled within 15 minutes at an assumed average speed. Walking accessibility was modelled with an average speed of 5 km/h, while cycling and the public transport proxy were modelled with an average speed of 15 km/h.

### Isochrone construction

For each mode of transport, all reachable network vertices within the 15-minute distance threshold were extracted. These vertices were converted into spatial point objects and transformed into EPSG:2056 to avoid geometric operations in geographic coordinates. The accessible area was then approximated by creating a convex hull around the reachable vertices. The resulting polygons were transformed back to WGS84 and stored as 15-minute isochrones for walking, cycling, and the public transport proxy.

This approach provides a simplified but transparent estimate of theoretical accessibility from home. However, the convex hull generalises the accessible area and may include spaces that are not directly reachable along the network. Therefore, the isochrones should be interpreted as approximate accessibility zones rather than exact travel-time polygons.

### Points of Interest extraction

To relate theoretical accessibility to the urban context, Points of Interest were extracted from OpenStreetMap. The POI categories were selected based on the daily activities relevant to the analysed individual. These categories included work, sport, university, groceries, restaurants and cafés, parks and forests, and health-related services such as pharmacies, doctors, and clinics. The work category was restricted to consulting and engineering offices, because these categories were more relevant for the mobility behaviour analysed in this project than a general office category.

The bounding box used for POI extraction was derived from the combined extent of all isochrones. POIs were downloaded with the `osmdata` package through Overpass API queries. Because OpenStreetMap features can be stored as points, polygons, or multipolygons, all retrieved geometries were converted into representative point geometries. Point geometries were kept unchanged, while polygon and multipolygon geometries were converted using point-on-surface operations. This ensured that all POIs could be analysed consistently as point features.

To reduce the risk of failed OpenStreetMap queries due to request size or server timeouts, the study area was divided into a 3 × 3 grid. POI queries were then performed separately for each grid cell. The results from all grid cells were combined into a single dataset, and duplicate features were removed based on the OpenStreetMap ID, POI category, and POI subcategory.

### Linking POIs to accessibility areas

After retrieving and cleaning the POI data, the POIs were spatially joined with the 15-minute isochrones using a within relationship. This allowed us to identify which POIs were located inside the theoretical accessibility areas of each transport mode. The number of accessible POIs was then summarised by transport mode, POI category, and POI subcategory. This step made it possible to compare the availability of nearby services across walking, cycling, and the public transport proxy.

### Visualisation and interpretation
Maybe next 2 paragraphs not usefull now since its only the intermediate maps etc
<!-- The resulting isochrones, street network, home location, and accessible POIs were visualised using interactive maps created with `mapview`. These maps were used to inspect the spatial relationship between the home location, the accessible areas, and the distribution of relevant services. The visual outputs form the basis for comparing theoretical 15-minute accessibility with actual mobility behaviour in later stages of the project. -->

<!-- Overall, this methodology embeds individual mobility data within its built environment context. The isochrone analysis represents what is theoretically accessible from home, while the POI analysis describes which activity-related services are available within these accessibility areas. In the next analytical step, these theoretical accessibility zones can be compared with the individual’s observed trajectories and annotated activities to identify mismatches between nearby available services and actual daily mobility patterns. -->
 
Ici continuer avec labellisation des trajectoires de Lucie + sf_join des deux codes etc

### Mobility Data 

The primary dataset used in this project consists of personal mobility records extracted from Google Timeline. The dataset covers approximately three months of movement behaviour in and around Zurich, Switzerland, and contains 1,336 observations representing both movement episodes and stationary visits. Each record includes temporal information, geographic coordinates and additional metadata describing either a movement segment or a visited location.

The Google Timeline dataset required substantial pre-processing before analysis. The original JSON file was imported into R and converted into a structured tabular dataset. Temporal information was extracted from the timestamps, including activity duration, date and weekday. Each observation was subsequently classified as either a movement episode or a visit episode. Records containing a value for travelled distance were classified as movements, whereas records containing a visit probability were classified as visits. Observations that contained neither attribute were labelled as unknown and excluded from subsequent analyses.

Geographic coordinates were extracted from the location strings and converted into spatial objects. All data were projected into the Swiss coordinate reference system CH1903+ / LV95 to ensure consistency with the remaining spatial datasets. Records with missing coordinate information were removed from the analysis.

A semantic annotation procedure was then implemented to transform raw locations into meaningful activity categories. Unique visited places were identified and manually classified using contextual information and map inspection. Locations were assigned to categories such as home, work, education, shopping, leisure, sport, nature, healthcare and social activities. Locations primarily representing transitions rather than destinations were reclassified as movement records. This semantic enrichment step transformed positional information into interpretable behavioural information and enabled subsequent activity-based analyses.

### Activity Space Analysis

To explore the spatial extent of mobility behaviour, activity spaces were constructed using convex hulls. Convex hulls were calculated for both the complete set of visited locations and for individual activity categories. This approach provides a simple representation of the geographical area associated with different activity types and allows comparisons between the spatial footprints of everyday activities.

### Accessibility Analysis

To address the first research question, visited locations were compared with the 15-minute accessibility areas. A spatial overlay was performed to determine whether each activity occurred within the walking, cycling or public transport isochrone. The proportion of activities occurring within each accessibility area was subsequently calculated for every activity category. This analysis quantifies the degree to which observed mobility behaviour aligns with the principles of the 15-minute city.

### Accessibility Gap Analysis

The second research question investigates whether the participant's activity patterns reflect the opportunities theoretically available within the 15-minute city. To address this question, activity categories derived from the mobility data were matched with corresponding Points of Interest (POI) categories extracted from OpenStreetMap. The analysis was restricted to the cycling-based isochrone, as cycling provides the largest accessibility area and therefore represents the most comprehensive interpretation of the 15-minute city concept. For each activity category, the proportion of observed visits occurring within the 15-minute cycling isochrone was compared with the proportion of accessible opportunities available within the same area. This comparison enabled the identification of accessibility gaps, defined as differences between the opportunities theoretically available to the participant and the destinations actually visited.

### Activities Beyond the 15-Minute City

The third research question examines which activities most frequently occur beyond the limits of the 15-minute city. Similar to the accessibility gap analysis, only the cycling-based isochrone was considered. Cycling was selected because it represents the broadest accessibility scenario and is commonly included in contemporary interpretations of the 15-minute city. For each activity category, the proportion of visits occurring outside the 15-minute cycling accessibility area was calculated. Categories with high proportions of visits beyond the cycling isochrone indicate activities that are less likely to be satisfied within the participant's local neighbourhood and therefore require travel beyond the spatial limits of the 15-minute city.

## Results

### Activity Spaces

[Insert Figure 1: Overall activity space and activity spaces by category]

Figure X presents the activity spaces derived from the visited locations. The overall activity space covers the Zurich metropolitan area and extends beyond the urban core for certain activity categories. Education, work and shopping activities are concentrated within a relatively small geographical area, whereas nature-related activities cover a substantially larger spatial extent. Leisure and social activities show intermediate spatial distributions. The category-specific activity spaces differ considerably in size and location. Some categories are represented by a small number of frequently visited locations, while others are distributed across a broader geographical area.

### Activities Within the 15-Minute City

[Insert Figure 2: Share of visits occurring within 15 minutes]

Figure X shows the proportion of visits occurring within the 15-minute accessibility areas for walking, cycling and public transport. The percentages vary across both transportation modes and activity categories.Cycling accessibility generally displays the highest proportions, followed by public transport and walking. Shopping, education and leisure activities show high shares of visits occurring within the 15-minute accessibility areas, whereas nature and social activities display lower values. The magnitude of these differences varies between transportation modes.

### Accessibility Gap

[Insert Figure 3: Observed use versus theoretical accessibility]

Figure X compares observed visits with the opportunities available within the cycling-based 15-minute accessibility area. The distribution of accessible opportunities differs across activity categories. For several categories, the proportion of available opportunities exceeds the proportion of observed visits. Other categories show a closer correspondence between available opportunities and visitation frequencies. The differences between observed behaviour and theoretical accessibility vary considerably across activity types.

### Activities Beyond the 15-Minute City

[Insert Figure 4: Activities beyond the cycling-based 15-minute city]

Figure X presents the proportion of visits occurring outside the cycling-based 15-minute accessibility area. The results show substantial variation between activity categories. Nature-related activities display the highest proportions of visits beyond the 15-minute threshold. Social and leisure activities also show relatively high values. In contrast, shopping and educational activities exhibit lower proportions of visits occurring beyond the cycling accessibility area.The distribution of activities beyond the 15-minute threshold is not uniform across activity categories and reflects distinct spatial patterns in the mobility dataset.

## Discussion

The objective of this project was to compare theoretical accessibility within a 15-minute city framework with observed mobility behaviour using personal movement data collected from Google Timeline. By combining mobility traces, semantic annotation, accessibility modelling and activity space analysis, the project provides insights into the relationship between available opportunities and actual destination choices.

The results indicate that a substantial proportion of daily activities can be performed within a 15-minute accessibility area, particularly when cycling is considered. Nevertheless, the accessibility gap analysis revealed that the existence of nearby opportunities does not necessarily imply their use.

Shopping activities provide a good example of this discrepancy. While numerous shopping opportunities are available within the participant's local neighbourhood, these opportunities largely consist of grocery stores. The shopping category used in this analysis also includes non-food retail activities, for which fewer local alternatives exist. Furthermore, grocery shopping is not primarily the responsibility of the participant within the household. As a result, many recorded shopping trips correspond to more specialised purchases and therefore occur outside the immediate neighbourhood. Cross-border shopping behaviour further contributes to this pattern, as neighbouring countries are frequently visited and often offer lower prices.

Nature-related activities also frequently occurred beyond the 15-minute accessibility area. However, the interpretation of this result requires some caution. Many local walks within the neighbourhood were recorded as movement episodes rather than visits and therefore were not included in the activity-based analysis. At the same time, the participant has a strong preference for hiking and mountain environments, resulting in frequent trips to destinations located in the Swiss Alps. This demonstrates how recreational preferences can influence mobility behaviour independently of local accessibility.

Social activities displayed a similar pattern. On the one side, social opportunities were harder to quantify within the local neighbourhood. On the other side, the geographical distribution of social networks strongly influences travel behaviour. As a foreign resident, the participant regularly travels to visit friends and family outside Switzerland. Even within Zurich, social activities often take place near the residences of friends rather than near the participant's home. In this case, destination choice is determined primarily by the location of social contacts rather than by accessibility considerations.

The results for leisure activities further illustrate the importance of social context. Restaurants, cultural events and other leisure destinations are frequently visited together with other people. The location of these activities is therefore often the result of collective decision-making rather than individual optimisation of travel distance. As a consequence, many leisure activities occur outside the local accessibility area despite local alternatives.

Educational activities are characterised by fixed destinations. During the study period, the participant attended two different universities whose locations were determined by programme availability and academic considerations rather than accessibility from home. Similarly, work-related travel was directed towards a fixed workplace located approximately twenty minutes away by bicycle or public transport. While this destination lies slightly beyond the 15-minute threshold, it remains relatively close compared with many other destinations observed in the dataset. These findings illustrate how institutional constraints can shape mobility behaviour.


Taken together, these observations suggest that accessibility alone provides an incomplete explanation of mobility behaviour. The results indicate that destination choice is influenced by a combination of accessibility, personal preferences, social relationships, institutional constraints and economic considerations. Consequently, the existence of nearby opportunities does not automatically result in local activity patterns.

From a Computational Movement Analysis perspective, the project demonstrates the value of semantic enrichment and contextual information. Although activity categories could potentially be inferred automatically using behavioural rules based on visit frequency, duration, time of day, day of the week or the surrounding Points of Interest, such approaches remain subject to uncertainty. For example, a long stay at a location between 8am and 5 pm on a work day could correspond to work, education or a social visit. Given the relatively small dataset and the exploratory nature of the project, manual semantic annotation was chosen to maximise classification accuracy. It is the integration of contextual information that transforms raw trajectories into meaningful representations of mobility behaviour and enables a more nuanced understanding of the relationship between urban structure and everyday activity patterns.

### Limitations 

Several limitations should be acknowledged. First, the analysis is based on the mobility behaviour of a single individual and therefore cannot be generalised to the broader population. The observed patterns may be strongly influenced by personal circumstances, lifestyle and preferences. Second, Google Timeline data contain positional uncertainty and may occasionally misclassify activities or transportation modes. Third, the semantic annotation process was conducted manually and therefore introduces a degree of subjectivity. Different classifications may have produced slightly different results.

A further limitation concerns the definition of activities. The analysis focuses on visited locations and therefore excludes movement episodes that do not result in a stationary visit. This particularly affects nature-related activities, as local walks were often classified as movement rather than visits. Consequently, some activities occurring within the local neighbourhood may be underrepresented in the final dataset.

The accessibility analysis itself also involves several methodological simplifications. Accessibility areas were approximated using convex hulls around reachable network vertices rather than exact travel-time polygons. While this approach provides a transparent and computationally efficient estimate of accessibility, it may overestimate the true accessible area by including locations that are not directly reachable within the specified travel time. Consequently, the number of theoretically accessible opportunities may be slightly overestimated.

The representation of public transport constitutes an additional limitation. Instead of modelling actual transit routes, stops, schedules and transfer times, public transport accessibility was approximated using a simplified network-based proxy. The resulting public transport isochrones should therefore be interpreted as approximate indicators of accessibility rather than realistic representations of public transport travel times.

Finally, the accessibility gap analysis is sensitive to how opportunities are defined and categorised. Points of Interest were selected and grouped according to categories considered relevant to the participant's daily activities. Different categorisation choices could have produced different estimates of accessibility. For example, local shopping opportunities are dominated by grocery stores, whereas observed shopping activities often correspond to more specialised forms of retail. The measured accessibility gap therefore partly depends on how activity categories are defined.

Future work could extend the analysis to multiple participants in order to investigate whether the observed patterns are specific to the individual or representative of broader urban populations. Additional analyses could also incorporate temporal dimensions, such as differences between weekdays and weekends, or explore how accessibility and behaviour vary across demographic groups. 

Overall, the results suggest that the 15-minute city provides a useful framework for evaluating accessibility, but accessibility alone is insufficient to explain observed mobility behaviour. While many routine activities occur within local accessibility areas, destination choice remains strongly influenced by factors extending beyond simple spatial proximity.

## Appendix

### Wordcount
```{r}
wordcountaddin::word_count("index.qmd")
#max character= 20000 ((incl. spaces, incl. References list, excl. Code listing)
```


