---
title: "Isochrones and Points of Interest"
author: "Noémie and Lucie"
format: html
---

## Load packages

```{r}
#| label: setup
#| message: false
#| warning: false

library(dodgr)
library(sf)
library(dplyr)
library(purrr)
library(osmdata)
library(mapview)
```

## Define origin and analysis area

```{r}
#| label: define-origin-and-bbox

# Home location in WGS84 coordinates
home_sf <- st_sf(
  geometry = st_sfc(st_point(c(8.546069, 47.409620))),
  crs = 4326
)

# Create a 6 km buffer around the home location and convert it to a bbox
bbox <- home_sf |>
  st_transform(2056) |>
  st_buffer(6000) |>
  st_transform(4326) |>
  st_bbox()
```

## Download street network

```{r}
#| label: download-street-network

# Download the OSM street network for the analysis area
routes <- dodgr_streetnet(bbox, expand = 0.1)
```

## Define helper functions for isochrones

```{r}
#| label: isochrone-helper-functions

# Identify the vertex ID column used by dodgr
get_vertex_id_col <- function(verts) {
  if ("id" %in% names(verts)) {
    return("id")
  }

  if ("vertex_id" %in% names(verts)) {
    return("vertex_id")
  }

  stop("Could not find the vertex ID column.")
}

# Match the origin point to the nearest connected network vertex
snap_to_vertex <- function(graph, origin_sf) {
  verts <- dodgr_vertices(graph)
  id_col <- get_vertex_id_col(verts)

  origin_xy <- st_coordinates(st_transform(origin_sf, 4326))
  origin_xy <- data.frame(
    x = origin_xy[, 1],
    y = origin_xy[, 2]
  )

  vertex_index <- match_pts_to_verts(
    verts,
    origin_xy,
    connected = TRUE
  )

  origin_vid <- verts[[id_col]][vertex_index]

  return(origin_vid)
}

# Create an isochrone polygon from a weighted dodgr network
make_isochrone <- function(graph, origin_sf, speed_kmh, minutes, mode_name) {

  # Extract vertices from the network
  verts <- dodgr_vertices(graph)
  id_col <- get_vertex_id_col(verts)

  # Snap the origin to the nearest connected vertex
  origin_vid <- snap_to_vertex(graph, origin_sf)

  # Calculate network distances from the origin vertex
  d_mat <- dodgr_dists(graph, from = origin_vid)

  # dodgr_dists returns a matrix, so convert it to a named vector
  d_vec <- as.numeric(d_mat[1, ])
  names(d_vec) <- colnames(d_mat)

  # Convert travel time and speed into a maximum reachable distance in metres
  dist_limit <- speed_kmh * (minutes / 60) * 1000

  # Select all reachable vertices within the distance threshold
  reachable_ids <- names(d_vec)[is.finite(d_vec) & d_vec <= dist_limit]

  nodes <- verts[
    as.character(verts[[id_col]]) %in% as.character(reachable_ids),
  ]

  # Return an empty geometry if too few vertices are reachable
  if (nrow(nodes) < 3) {
    message("No isochrone created for ", mode_name, ": fewer than 3 reachable nodes.")

    return(st_sf(
      mode = mode_name,
      speed_kmh = speed_kmh,
      minutes = minutes,
      n_nodes = nrow(nodes),
      geometry = st_sfc(st_geometrycollection(), crs = 4326)
    ))
  }

  # Convert reachable vertices to sf points
  pts <- st_as_sf(
    nodes,
    coords = c("x", "y"),
    crs = 4326,
    remove = FALSE
  )

  # Create a convex hull in LV95 to avoid geometric operations in degrees
  iso_geom <- pts |>
    st_transform(2056) |>
    st_geometry() |>
    st_union() |>
    st_convex_hull() |>
    st_transform(4326)

  iso <- st_sf(
    mode = mode_name,
    speed_kmh = speed_kmh,
    minutes = minutes,
    n_nodes = nrow(nodes),
    origin_vid = as.character(origin_vid),
    geometry = iso_geom
  )

  return(iso)
}
```

## Build weighted transport networks

```{r}
#| label: build-weighted-networks

# Walking network
graph_walk <- weight_streetnet(
  routes,
  wt_profile = "foot"
)

# Cycling network
graph_bike <- weight_streetnet(
  routes,
  wt_profile = "bicycle"
)

```

## Create 15-minute isochrones

```{r}
#| label: create-isochrones

# 15-minute walking isochrone, assuming 5 km/h
iso_walk <- make_isochrone(
  graph = graph_walk,
  origin_sf = home_sf,
  speed_kmh = 5,
  minutes = 15,
  mode_name = "Walking"
)

# 15-minute cycling isochrone, assuming 15 km/h
iso_bike <- make_isochrone(
  graph = graph_bike,
  origin_sf = home_sf,
  speed_kmh = 15,
  minutes = 15,
  mode_name = "Cycling"
)


# Combine all isochrones and remove empty geometries
iso_all <- rbind(iso_walk, iso_bike) |>
  st_make_valid()

iso_all <- iso_all[!st_is_empty(iso_all), ]

# Quick check of the created isochrones
iso_all[, c("mode", "speed_kmh", "minutes", "n_nodes")]
```

## Define POI categories

The POI categories were selected based on the activities of the individual whose mobility trajectories are analysed. The aim is not to include all possible urban services in Zurich, but to focus on places that are relevant for this person’s daily life, such as work, groceries, sport, restaurants, parks or forests, university, and health-related services.

The work category was limited to consulting and engineering offices, because these types of workplaces are more relevant for the analysed mobility patterns than a general office category. However, all POI categories depend on how places are labelled in OpenStreetMap. Some places may be missing, wrongly classified, or labelled in a very general way. Therefore, the POI analysis should be understood as an approximation of accessible services rather than a complete representation of all available places.

```{r}
#| label: define-poi-queries

poi_queries <- tibble::tribble(
  ~category,           ~subcategory,              ~key,          ~value,            ~key2,     ~value2,

  # Work
  "Work",              "Consulting office",       "office",      "consulting",      NA,        NA,
  "Work",              "Engineering office",      "office",      "engineer",        NA,        NA,

  # Sport
  "Sport",             "Swimming sports centre",  "leisure",     "sports_centre",   "sport",   "swimming",
  "Sport",             "Public bath",             "amenity",     "public_bath",     NA,        NA,
  "Sport",             "Water park",              "leisure",     "water_park",      NA,        NA,
  "Sport",             "Fitness centre",          "leisure",     "fitness_centre",  NA,        NA,

  # University
  "University",        "University",              "amenity",     "university",      NA,        NA,

  # Groceries
  "Groceries",         "Supermarket",             "shop",        "supermarket",     NA,        NA,
  "Groceries",         "Convenience store",       "shop",        "convenience",     NA,        NA,

  # Restaurants
  "Restaurants",       "Restaurant",              "amenity",     "restaurant",      NA,        NA,
  "Restaurants",       "Cafe",                    "amenity",     "cafe",            NA,        NA,

  # Park and forest
  "Park / forest",     "Park",                    "leisure",     "park",            NA,        NA,
  "Park / forest",     "Forest / wood",           "natural",     "wood",            NA,        NA,

  # Health-related services
  "Pharmacy / doctor", "Pharmacy",                "amenity",     "pharmacy",        NA,        NA,
  "Pharmacy / doctor", "Doctors",                 "amenity",     "doctors",         NA,        NA,
  "Pharmacy / doctor", "Doctor",                  "healthcare",  "doctor",          NA,        NA,
  "Pharmacy / doctor", "Clinic",                  "amenity",     "clinic",          NA,        NA
)
```

## Define helper functions for POI download

```{r}
#| label: poi-helper-functions

# Keep only point features that truly match the requested OSM tags
filter_real_points <- function(x, key, value, key2 = NA, value2 = NA) {

  if (is.null(x) || nrow(x) == 0) {
    return(NULL)
  }

  if (!(key %in% names(x))) {
    return(NULL)
  }

  keep <- !is.na(x[[key]])

  if (!is.na(value)) {
    keep <- keep & x[[key]] == value
  }

  if (!is.na(key2)) {
    if (!(key2 %in% names(x))) {
      return(NULL)
    }

    keep <- keep & !is.na(x[[key2]])

    if (!is.na(value2)) {
      keep <- keep & x[[key2]] == value2
    }
  }

  x <- x[keep, ]

  if (nrow(x) == 0) {
    return(NULL)
  }

  return(x)
}

# Convert polygon and multipolygon POIs to representative points
safe_to_points <- function(x, source_type) {

  if (is.null(x) || nrow(x) == 0) {
    return(NULL)
  }

  x <- st_make_valid(x)

  geom_types <- unique(as.character(st_geometry_type(x)))

  if (all(geom_types %in% c("POINT", "MULTIPOINT"))) {
    pts <- x
  } else {
    pts <- suppressWarnings(
      x |>
        st_transform(2056) |>
        st_point_on_surface() |>
        st_transform(4326)
    )
  }

  pts$source_geometry <- source_type

  return(pts)
}

# Download POIs for one OSM tag combination
get_pois <- function(bbox, key, value = NA, category, subcategory = NA,
                     key2 = NA, value2 = NA, timeout = 90) {

  message(
    "Downloading POI: ", category, " / ", subcategory,
    " | ", key, " = ", value
  )

  q <- opq(
    bbox = bbox,
    timeout = timeout
  )

  if (is.na(value)) {
    q <- q |>
      add_osm_feature(key = key)
  } else {
    q <- q |>
      add_osm_feature(key = key, value = value)
  }

  if (!is.na(key2)) {
    if (is.na(value2)) {
      q <- q |>
        add_osm_feature(key = key2)
    } else {
      q <- q |>
        add_osm_feature(key = key2, value = value2)
    }
  }

  osm <- tryCatch(
    {
      osmdata_sf(q)
    },
    error = function(e) {
      message("OSM query failed for: ", key, " = ", value)
      message("Reason: ", e$message)
      return(NULL)
    }
  )

  if (is.null(osm)) {
    return(NULL)
  }

  # Filter point objects before using them
  real_points <- filter_real_points(
    osm$osm_points,
    key = key,
    value = value,
    key2 = key2,
    value2 = value2
  )

  # Convert all geometries to point geometries
  poi_parts <- list(
    safe_to_points(real_points, "point"),
    safe_to_points(osm$osm_polygons, "polygon"),
    safe_to_points(osm$osm_multipolygons, "multipolygon")
  )

  poi_parts <- poi_parts[
    purrr::map_lgl(poi_parts, ~ !is.null(.x) && nrow(.x) > 0)
  ]

  if (length(poi_parts) == 0) {
    message("No POI found for: ", key, " = ", value)
    return(NULL)
  }

  pois <- bind_rows(poi_parts) |>
    mutate(
      poi_category = category,
      poi_subcategory = subcategory,
      osm_key = key,
      osm_value = ifelse(is.na(value), "any", value)
    )

  return(pois)
}
```

## Create a grid for smaller OSM queries

```{r}
#| label: create-poi-query-grid

# Create a bbox around all isochrones
poi_bbox <- iso_all |>
  st_transform(4326) |>
  st_bbox()

# Convert bbox to polygon
poi_area <- st_as_sfc(poi_bbox) |>
  st_sf(crs = 4326)

# Split the bbox into a 3 x 3 grid to reduce the risk of OSM gateway timeouts
grid_geom <- st_make_grid(
  poi_area,
  n = c(3, 3),
  what = "polygons"
)

bbox_grid <- st_sf(
  grid_id = seq_along(grid_geom),
  geometry = grid_geom,
  crs = 4326
)

# Keep only grid cells that intersect the analysis area
bbox_grid <- bbox_grid[
  st_intersects(bbox_grid, poi_area, sparse = FALSE),
]

mapview(bbox_grid)
```

## Download POIs by grid cell

```{r}
#| label: download-pois-by-grid

get_pois_for_grid <- function(grid_sf, poi_queries) {

  results <- list()
  counter <- 1

  for (i in seq_len(nrow(grid_sf))) {

    tile_bbox <- st_bbox(grid_sf[i, ])

    message("Processing grid cell ", i, " / ", nrow(grid_sf))

    tile_results <- pmap(
      list(
        poi_queries$key,
        poi_queries$value,
        poi_queries$category,
        poi_queries$subcategory,
        poi_queries$key2,
        poi_queries$value2
      ),
      function(key, value, category, subcategory, key2, value2) {

        # Small pause to avoid sending too many requests at once
        Sys.sleep(0.5)

        get_pois(
          bbox = tile_bbox,
          key = key,
          value = value,
          category = category,
          subcategory = subcategory,
          key2 = key2,
          value2 = value2,
          timeout = 90
        )
      }
    )

    tile_results <- tile_results[
      purrr::map_lgl(tile_results, ~ !is.null(.x) && nrow(.x) > 0)
    ]

    if (length(tile_results) > 0) {
      results[[counter]] <- bind_rows(tile_results)
      counter <- counter + 1
    }
  }

  if (length(results) == 0) {
    return(NULL)
  }

  pois <- bind_rows(results) |>
    distinct(osm_id, poi_category, poi_subcategory, .keep_all = TRUE)

  return(pois)
}

pois_tous <- get_pois_for_grid(
  grid_sf = bbox_grid,
  poi_queries = poi_queries
)

if (is.null(pois_tous) || nrow(pois_tous) == 0) {
  stop("No POIs were downloaded. Check the OSM queries or the bbox.")
}

pois_tous <- st_as_sf(pois_tous)
```

## Join POIs to isochrones

```{r}
#| label: join-pois-to-isochrones

pois_by_iso <- st_join(
  pois_tous,
  iso_all[, c("mode", "speed_kmh", "minutes")],
  join = st_within,
  left = FALSE
)

# Count POIs by isochrone mode and category
pois_by_iso |>
  st_drop_geometry() |>
  count(mode, poi_category, poi_subcategory, sort = TRUE)
```

## Visualise POIs and isochrones


## Visualise POIs with categorical colours

```{r}
#| label: visualise-pois-categorical

# Convert subcategories to a factor for categorical colouring
pois_by_iso$poi_subcategory <- as.factor(pois_by_iso$poi_subcategory)

# Create one colour per POI subcategory
set.seed(123)

poi_levels <- levels(pois_by_iso$poi_subcategory)

poi_colors <- sample(
  grDevices::rainbow(length(poi_levels), s = 0.8, v = 0.9)
)

```

## Export outputs

```{r}
#| label: export-outputs

# Create output folder
dir.create("outputs", showWarnings = FALSE)

# Make sure geometries are valid before export
iso_all <- iso_all |>
  st_make_valid()

pois_by_iso <- pois_by_iso |>
  st_make_valid()

# Save isochrones and POIs as R objects
saveRDS(iso_all, "outputs/isochrones_15min.rds")
saveRDS(pois_by_iso, "outputs/pois_by_iso.rds")

```
